---
title: "Data description"
output: 
  html_document:
    code_folding: hide
    df_print: paged
---

<!-- Set up workspace -->

```{r setup, include=FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Swipe environment
  rm(list=ls())
  
# Load packages
  library(kableExtra)
  library(XLConnect)
  library(XLConnectJars)
  
```

<br>

We created a tab for every data set used within this paper which displays variables' meaning und their value codes:

  + qn_data
  + EEG_task_data
  + ERP_data
  + ERPs_Topo_Face1
  + ERPs_Topo_Face2
  + ERP_Traj_Face_1 (ROI_P1_P3_Face1, left_ROI_N170_Face1, right_ROI_N170_Face1)
  + ERP_Traj_Face_2 (ROI_P1_P3_Face2, left_ROI_N170_Face2, right_ROI_N170_Face2)
  + EMT
  
### Overview of data sets  {.tabset .tabset-pills}

#### qn_data

<!-- Display qn_data descriptions -->  
  
```{r table_qn_data}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx", 
                               sheet = "qn_data", 
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```
  


#### EEG task data

<!-- Display EEG task descriptions -->  

```{r table_eeg_task_data}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "EEG_task_data",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```


#### ERP_data

<!-- Display ERP data descriptions -->  


```{r table_ERPs}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERP_data",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```



#### ERP_Topo_Face1

<!-- Display ERP data descriptions -->  

```{r table_ERP_topo_f1}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERP_Topo_Face1",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```



#### ERP_Topo_Face2

<!-- Display ERP data descriptions -->  


```{r table_ERP_topo_f2}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERP_Topo_Face2",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```



#### ERP_Traj_Face1

<!-- Display ERP data descriptions -->  


```{r table_ERP_traj_f1}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERP_Traj_Face1",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```




#### ERP_Traj_Face2

<!-- Display ERP data descriptions -->  


```{r table_ERP_traj_f2}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERP_Topo_Face2",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```





#### EMT

<!-- Display EMT task data descriptions -->  

```{r table_EMT}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "EMT_data",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 12,fixed_thead = T)

```


### Session info

<!-- Provide session info  -->

```{r session_info, results = TRUE}

# Get session info 
  sessionInfo()

```

