---
title: "Data description"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE, echo=FALSE}

# Set general settings for Markdown file 
  options(max.print="75")
  knitr::opts_chunk$set(echo=TRUE,
  	             #cache=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE)
  knitr::opts_knit$set(width=75)
  
# Load packages
  library(kableExtra)
  library(XLConnect)
  library(rmdformats)

# Swipe environment
  rm(list=ls())

```

# Introduction 

In 'Overview of data sets', we created a tab for every data set used within this paper which displays variables' meaning and their value codes:

  + qn_data
  + EEG_task_data
  + ERP_data
  + ERPs_Topo_Face1
  + ERPs_Topo_Face2
  + XX_ROI_XX_Face_1 (ROI_P1_P3_Face1, left_ROI_N170_Face1, right_ROI_N170_Face1)
  + XX_ROI_XX_Face_2 (ROI_P1_P3_Face2, left_ROI_N170_Face2, right_ROI_N170_Face2)
  + EMT_data
  
# Overview of data sets {.tabset .tabset-pills}

## qn_data

<!-- Display qn_data descriptions -->  
  
```{r table_qn_data, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx", 
                               sheet = "qn_data", 
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```
  
  
## EEG task data

<!-- Display EEG task descriptions -->  

```{r table_eeg_task_data, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "EEG_task_data",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


## ERP_data

<!-- Display ERP data descriptions -->  


```{r table_ERPs, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERP_data",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


## ERP_Topo_Face1

<!-- Display ERP data descriptions -->  

```{r table_ERP_topo_f1, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERPs_Topo_Face1",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


## ERPs_Topo_Face2

<!-- Display ERP data descriptions -->  


```{r table_ERP_topo_f2, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "ERPs_Topo_Face2",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


## XX_ROI_XX_Face_1

<!-- Display ERP data descriptions -->  


```{r table_ERP_traj_f1, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "XX_ROI_XX_Face1",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


## XX_ROI_XX_Face_2

<!-- Display ERP data descriptions -->  


```{r table_ERP_traj_f2, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "XX_ROI_XX_Face2",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


## EMT data

<!-- Display EMT task data descriptions -->  

```{r table_EMT, results = 'asis'}

# Load data set
  qn_data_desc = readWorksheetFromFile("./data/data_overview.xlsx",
                               sheet = "EMT_data",
                               startCol = 1,
                               endCol = 0)

# Create table
  kable(qn_data_desc) %>%
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)

```


# Session info

<!-- Provide session info  -->

```{r session_info, results = TRUE}

# Get session info 
  sessionInfo()

```

