---
title: "Delayed match-to-sample task"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  options(max.print="75")

  knitr::opts_chunk$set(echo=TRUE,
  	             #cache=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE,
  	             fig.align="center",
  	             fig.width=6, fig.height=4)
  knitr::opts_knit$set(width=75)
  
# Swipe environment
  rm(list=ls())
  
# Set libraries
  library(cowplot)
  library(dplyr)
  library(eeptools)
  library(EnvStats)
  library(ez)
  library(ggplot2)
  library(ggstatsplot)
  library(Hmisc)
  library(kableExtra)
  library(lme4)
  library(lmerTest)
  library(MASS)
  library(miceadds)
  library(multcomp)
  library(psych)
  library(reshape2)
  library(Rmisc)
  library(sjPlot)
  library(sjmisc)
  library(sjlabelled)
  library(tidyverse)

# Load overdispersion function
  overdisp_fun = function(model) {
    rdf = df.residual(model)
    rp = residuals(model,type="pearson")
    Pearson.chisq = sum(rp^2)
    prat = Pearson.chisq/rdf
    pval = pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
  }
  
# Raincloud plot function   
  source("./functions/geom_flat_violin.R")
  
# Round to 2 digits   
  options(digits=2)
  
# Disable scientific notation in R
  options(scipen = 999)
  
# Set figure theme  
  theme_SN = theme(axis.title.y = element_text(size = 13, margin = margin(t = 0, r = 20, b = 0, l = 0)),
          panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "black", linetype = "dotted", size=0.6),
          panel.grid.minor.y = element_blank(),
          panel.background = element_rect(colour = "black", size = 0.5),
          text=element_text(size = 12),
          legend.position = "none")
  
# Set figure color palettes
  emotion_col = c("#99bada","#3375b5","#003162")
  nov_col = c("#2FA9F5","#134462")
  
# Round p-values   
  reportP = function(pValue){
    if (pValue < 0.001){
      result = "*p* < 0.001"
    } else {
      result = sprintf("*p* = %.2f", pValue) # inserts a float into a string and simultaneously do rounding
    }
    return(result)
  }  
  
# Beta values
  reportbe = function(pValue){
    if (0 <= pValue & pValue <= 0.01 ){
      result = "< 0.01"
    } 
    else if (pValue < 0){
      result = sprintf("= %.2f", pValue)
    }
    else {
      result = sprintf("= %.2f", pValue) # inserts a float into a string and simultaneously do rounding
    }
    return(result)
  }  
  
# CI values
  reportci = function(pValue){
    if (0 <= pValue & pValue <= 0.01 ){
      result = "< 0.01"
    } 
    else if (pValue < 0){
      result = sprintf("%.2f", pValue)
    }
    else {
      result = sprintf("%.2f", pValue) # inserts a float into a string and simultaneously do rounding
    }
    return(result)
  }    
  
```

<!-- Load data set-->

```{r load_data, include = FALSE}

# Load EEG task data
  load.Rdata(filename="./data/EEG_task_data.Rdata", "EEG_task_data")

# Scale WM
  EEG_task_data$WM_scal = scale(EEG_task_data$WM)
  
```

# Task description

<<<<<<< HEAD
Our EEG paradigm was comprised of a delayed match-to-sample task in which children had do indicate whether Face 1 and Face 2 showed the same (`repeated`) or a different emotional facial expression (`novel`). Besides their EEG, we measured participants' accuracy rates and reaction times. 
=======
Our EEG paradigm included a delayed same-different matching task in which children had do indicate whether Face 1 and Face 2 showed the same (`repeated`) or a different emotional facial expression (`novel`). We measured participants' accuracy rates and reaction times. 

We excluded: 

  + Reaction times < 250 ms or >  7s
  + Values </> 2.5 of the median absolute deviation (MAD) based on the individual participant
  + Incorrect answers
  + Rejected EEG trials
  
We calculated general linear mixed models (GLMM) for accuracy rates and linear mixed models (LMM) for reaction times. Fixed effects are defined for each model individually.  As fixed factors, all models included treatment contrasts for *facial expressions* (`emotional [average of happy/angry] vs. neutral faces (Emo_Neu)`, `happy vs. angry faces (Hap_Ang)`), *repetition* (`novel vs. repeated emotion trials (Rep_Nov)`) as well as their interaction (`Emo_NeuxRep_Nov, Hap_AngxRep_Nov`). Due to the high cognitive task demands, working memory  (`WM_scal`) was entered as scaled covariate in all (general) linear mixed model analyses.
>>>>>>> master

We excluded reaction times < 250 ms and incorrect trials. Subsequently, we calculated general linear mixed models (GLMM) for accuracy rates and linear mixed models (LMM) for reaction times. Fixed effects are defined for each model individually.  As fixed factors, all models included treatment contrasts for *facial expressions* (`emotional [average of happy/angry] vs. neutral faces (Emo_Neu)`, `happy vs. angry faces (Hap_Ang)`), *repetition* (`novel vs. repeated emotion trials (Rep_Nov)`) as well as their interaction (`Emo_NeuxRep_Nov, Hap_AngxRep_Nov`). Due to the high cognitive task demands, working memory  (`WM_scal`) was entered as scaled covariate in all (general) linear mixed model analyses.

<<<<<<< HEAD
The random effects structure included random intercepts for participants `(1|ID)` and stimulus `(1|Stim_Type)`. Assumptions for multiple regression were checked for all models (normality of the residuals, linearity, multicollinearity, homoscedasticity). 
=======
Assumptions for multiple regression were checked for all models (normality of the residuals, linearity, multicollinearity, homoscedasticity). 
>>>>>>> master

We expected children to be faster and more accurate when Face 1 and Face 2 showed different emotions. Additionally, we expected the highest accuracy rates and fastest reaction times for pairings with happy facial expressions.

# Accuracy & Reaction times

#### **Descriptive statistics** 

Accuracy rates (left side) and reaction times (right side) of the delayed match-to-sample task. Error bars indicate standard errors (SE).
<<<<<<< HEAD

```{r EEG_Acc_RT_plots, results = TRUE, fig.width = 8, fig.height = 4}

## Plot accuracy rates 
  EEG_task_Acc_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE & Response == 1)

=======

```{r EEG_Acc_RT_plots, results = TRUE}

## Plot accuracy rates 

# Load EEG task data
  load.Rdata(filename="./data/EEG_task_data.Rdata", "EEG_task_data")

## Plot accuracy rates 

# Select outlier-free data and correct trials
  EEG_task_Acc_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE 
                             & Exclude_larger_7s == FALSE 
                             & Exclude_MAD == FALSE
                             & EEG_trial_loss == 1)

  EEG_task_Acc_plot = subset(EEG_task_Acc_plot, Response == 1)
  
>>>>>>> master
# Rename variables
  EEG_task_Acc_plot$Cong[EEG_task_Acc_plot$Cong == 1] = "repeated"
  EEG_task_Acc_plot$Cong[EEG_task_Acc_plot$Cong == 2] = "novel"

  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==4] = "happy"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==5] = "neutral"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==6] = "angry"
  
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==7] = "happy"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==8] = "neutral"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==9] = "angry"
<<<<<<< HEAD

# Get accuracy for novel and repeated Target
  acc_all = data.frame(xtabs(~ID+Cong+Target, EEG_task_Acc_plot))

# Recode to accuracy in percent (72 novel trials, 72 repeated trials, divided by three for three emotion conditions)
  acc_all$Freq = (acc_all$Freq/24)*100

=======

# Get accuracy for novel and repeated Target
  acc_all = data.frame(xtabs(~ID+Cong+Target, EEG_task_Acc_plot))

# Recode to accuracy in percent (72 novel trials, 72 repeated trials, divided by three for three emotion conditions)
  acc_all$Freq = (acc_all$Freq/24)*100

>>>>>>> master
# Factor Target
  acc_all$Cong = as.factor(acc_all$Cong)
  acc_all$Target = as.factor(acc_all$Target)

# Calculate descriptives on accuracy
  stats_acc_all = summarySEwithin(acc_all, measurevar="Freq", withinvars=c("Cong","Target"), idvar = "ID")

# Plot accuracy
  EEG_acc_plot = ggplot(stats_acc_all, aes(x=Target, y=Freq, fill = Cong)) +
    geom_bar(position=position_dodge(), stat="identity",colour="black", size=0.4,width=0.9) +
    geom_errorbar(aes(ymin=Freq-se, ymax=Freq+se), size=0.4, width=0.2, position=position_dodge(.9)) +
    labs (x= "", y = "Accuracy [%]") +
    scale_fill_manual(name = "Repetition", values=nov_col)+
<<<<<<< HEAD
    coord_cartesian(ylim = c(0, 80)) +
=======
    coord_cartesian(ylim = c(0, 65)) +
>>>>>>> master
    scale_y_continuous(breaks=seq(0,100,20))+
    theme_bw()+
    theme_SN +
    theme(legend.position = "top", legend.direction = "vertical",
           legend.key.size = unit(1, "cm"),
           legend.key.width = unit(0.5,"cm"))
   
## RT plot
<<<<<<< HEAD

# Choose outlier-free and correct trial data
  EEG_task_RT_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE)
  
  EEG_task_RT_plot = subset(EEG_task_RT_plot, Response == 1)

# Rename variables
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==1] = "repeated"
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==2] = "novel"

  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==4] = "happy"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==5] = "neutral"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==6] = "angry"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==7] = "happy"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==8] = "neutral"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==9] = "angry"
  
  stats_RT_all = summarySEwithin(EEG_task_RT_plot, measurevar="RTs", withinvars=c("Cong","Target"), idvar = "ID")
  
# Plot RTs
  EEG_RT_plot =
    ggplot(stats_RT_all, aes(x = Target, y = RTs, fill = Cong)) +
    geom_bar(position=position_dodge(), stat="identity", colour="black", size=0.4, width=0.9) +
    geom_errorbar(aes(ymin=RTs-se, ymax=RTs+se), size=0.4, width=0.2, position=position_dodge(.9)) +
    labs (x= "", y = "RT [ms]") +
    coord_cartesian(ylim = c(0, 3000)) +
    scale_y_continuous(breaks=seq(0,3000,500))+
    scale_fill_manual(values=nov_col)+
    theme_bw()+
    theme_SN+
    theme(legend.position = "none", legend.title=element_blank())

# Put plots together
  plots_Acc_RT = cowplot::plot_grid(
    EEG_acc_plot + theme(legend.position="none"),
    EEG_RT_plot + theme(legend.position="none"),
    align = 'vh',
    hjust = -1,
    nrow = 1)

# Get legend
  legend_Acc_RT = get_legend(EEG_acc_plot  +
    theme(legend.box.margin = margin(0, 0, 0, 2)))

# Display plot
# https://wilkelab.org/cowplot/articles/shared_legends.html
  fig_EEG_Acc_RT = cowplot::plot_grid(plots_Acc_RT, legend_Acc_RT, rel_widths = c(1, .2))
  fig_EEG_Acc_RT
  
  
# Save figure for publication   
  #ggsave("Figure_X_DMTST_perf.tiff", plot = last_plot(), dpi = 300)
  
=======

# Choose outlier-free and correct trial data
  EEG_task_RT_plot = subset(EEG_task_data,Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE 
                            & Exclude_MAD == FALSE)  
  EEG_task_RT_plot = subset(EEG_task_RT_plot, Response == 1)

# Rename variables
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==1] = "repeated"
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==2] = "novel"
  
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==4] = "happy"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==5] = "neutral"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==6] = "angry"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==7] = "happy"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==8] = "neutral"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==9] = "angry"
  
  stats_RT_all = summarySEwithin(EEG_task_RT_plot, measurevar="RTs", withinvars=c("Cong","Target"), idvar = "ID")
  
# Plot RTs
  EEG_RT_plot =
    ggplot(stats_RT_all, aes(x = Target, y = RTs, fill = Cong)) +
    geom_bar(position=position_dodge(), stat="identity", colour="black", size=0.4, width=0.9) +
    geom_errorbar(aes(ymin=RTs-se, ymax=RTs+se), size=0.4, width=0.2, position=position_dodge(.9)) +
    labs (x= "", y = "RT [ms]") +
    coord_cartesian(ylim = c(0, 1700)) +
    scale_y_continuous(breaks=seq(0,2000,500))+
    scale_fill_manual(values=nov_col)+
    theme_bw()+
    theme_SN+
    theme(legend.position = "none", legend.title=element_blank())

# Put plots together
  plots_Acc_RT = cowplot::plot_grid(
    EEG_acc_plot + theme(legend.position="none"),
    EEG_RT_plot + theme(legend.position="none"),
    align = 'vh',
    hjust = -1,
    nrow = 1)

# Get legend
  legend_Acc_RT = get_legend(EEG_acc_plot  +
    theme(legend.box.margin = margin(0, 0, 0, 2)))

# Display plot
# https://wilkelab.org/cowplot/articles/shared_legends.html
  fig_EEG_Acc_RT = cowplot::plot_grid(plots_Acc_RT, legend_Acc_RT, rel_widths = c(1, .2))
  fig_EEG_Acc_RT
>>>>>>> master

```

#### **Model specifications** 

##### Accuray rate GLMM: {.tabset .tabset-pills}

<!-- GLMM model specifications -->

###### Random effect structure 
<<<<<<< HEAD

We fitted single-trial data to the following model:

```{r EEG_Acc_GLMM_res}

# Select outlier-free data
  EEG_task_Acc_glmm = subset(EEG_task_data, Exclude_smaller_250ms == FALSE)
=======

We fitted single-trial data to the following model:

```{r EEG_Acc_GLMM_res}

# Scale working memory
  EEG_task_data$WM_scal = scale(EEG_task_data$WM)

# Select outlier-free data
  EEG_task_Acc_glmm = subset(EEG_task_data,Exclude_smaller_250ms == FALSE 
                             & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE 
                             & EEG_trial_loss == 1)
>>>>>>> master

# Factor random effects
  EEG_task_Acc_glmm$ID = as.factor(EEG_task_Acc_glmm$ID)
  EEG_task_Acc_glmm$Stim_Type = as.factor(EEG_task_Acc_glmm$Stim_Type)

# Define novel vs repeated trials
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 4]='c_happy';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 5]='c_neutral';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 6]='c_angry';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 7]='ic_happy';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 8]='ic_neutral';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 9]='ic_angry';

# Create one variable for emotion and one for repetition 
  EEG_task_Acc_glmm$emot[(EEG_task_Acc_glmm$Target == 'c_happy')  | (EEG_task_Acc_glmm$Target == 'ic_happy')] = 1
  EEG_task_Acc_glmm$emot[(EEG_task_Acc_glmm$Target == 'c_angry')  | (EEG_task_Acc_glmm$Target == 'ic_angry')] = 2
  EEG_task_Acc_glmm$emot[(EEG_task_Acc_glmm$Target == 'c_neutral')  | (EEG_task_Acc_glmm$Target == 'ic_neutral')] = 3
<<<<<<< HEAD
  
  EEG_task_Acc_glmm$rep[(EEG_task_Acc_glmm$Target == 'c_happy')  
                        | (EEG_task_Acc_glmm$Target == 'c_angry') 
                        | (EEG_task_Acc_glmm$Target == 'c_neutral')] = 1
  EEG_task_Acc_glmm$rep[(EEG_task_Acc_glmm$Target == 'ic_happy')  
                        | (EEG_task_Acc_glmm$Target == 'ic_angry') 
                        | (EEG_task_Acc_glmm$Target == 'ic_neutral')] = 2

# Rename variables   
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 1]='happy';
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 2]='angry';
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 3]='neutral';
  EEG_task_Acc_glmm$rep[EEG_task_Acc_glmm$rep == 1]='repeated';
  EEG_task_Acc_glmm$rep[EEG_task_Acc_glmm$rep == 2]='novel';

# Factor emotion and repetition variable
  EEG_task_Acc_glmm$rep = factor(EEG_task_Acc_glmm$rep)
  EEG_task_Acc_glmm$emot = factor(EEG_task_Acc_glmm$emot) 

# Create contrasts 
  contrasts(EEG_task_Acc_glmm$rep) = c(-0.5,0.5) # intercept is the mean of happy and angry
  contrasts(EEG_task_Acc_glmm$emot) = contr.treatment(3,  base = 3)

# A = angry, N = neutral, H = happy
  HvsA = c(0.5,-0.5,0) # compare: happy vs. angry
  EvsN = c(-0.25,-0.25,0.5) # compare happy/angry to neutral 
=======
  
  EEG_task_Acc_glmm$rep[(EEG_task_Acc_glmm$Target == 'c_happy')  
                        | (EEG_task_Acc_glmm$Target == 'c_angry') 
                        | (EEG_task_Acc_glmm$Target == 'c_neutral')] = 1
  EEG_task_Acc_glmm$rep[(EEG_task_Acc_glmm$Target == 'ic_happy')  
                        | (EEG_task_Acc_glmm$Target == 'ic_angry') 
                        | (EEG_task_Acc_glmm$Target == 'ic_neutral')] = 2

# Rename variables   
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 1]='happy';
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 2]='angry';
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 3]='neutral';
  EEG_task_Acc_glmm$rep[EEG_task_Acc_glmm$rep == 1]='repeated';
  EEG_task_Acc_glmm$rep[EEG_task_Acc_glmm$rep == 2]='novel';

# Factor emotion and repetition variable
  EEG_task_Acc_glmm$rep = factor(EEG_task_Acc_glmm$rep)
  EEG_task_Acc_glmm$emot = factor(EEG_task_Acc_glmm$emot) 

# Create contrasts 
  contrasts(EEG_task_Acc_glmm$rep) = contr.treatment(2,  base = 1)
  contrasts(EEG_task_Acc_glmm$emot) = contr.treatment(3,  base = 3)

# A = angry, N = neutral, H = happy
  HvsA = c(0.5,-0.5,0)
  EvsN = c(0.5,0.5,0)
  contrasts(EEG_task_Acc_glmm$emot) = cbind(EvsN,HvsA)
  
# Add contrast columns
  mm_EEG_task_Acc =  model.matrix( ~ emot*rep, EEG_task_Acc_glmm)   
  
# Attach to dataframe
  EEG_task_Acc_glmm[,(ncol(EEG_task_Acc_glmm)+1):(ncol(EEG_task_Acc_glmm)+6)] = mm_EEG_task_Acc
  names(EEG_task_Acc_glmm)[(ncol(EEG_task_Acc_glmm)-5):ncol(EEG_task_Acc_glmm)] = c("Mean","Emo_Neu", "Hap_Ang",
                                                                                    "Rep_Nov", "Emo_NeuxRep_Nov",
                                                                                    "Hap_AngxRep_Nov") 
# Build full model
  mod_Acc_EEG.glmm1 = glmer(Response ~ Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                            (1 + Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov||ID) +
                            (1 + Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov||Stim_Type),
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)

## Check random effect structure (cut-off: 0.005 - 0.001)

# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_Acc_EEG.glmm1))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_Acc_EEG.glmm1),comp = "Variance")
  

# Adapt model
  mod_Acc_EEG.glmm2 = glmer(Response ~ Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                            (1 + Hap_Ang + Rep_Nov ||ID) +
                            (0 + Emo_Neu + Hap_Ang + Rep_Nov + Hap_AngxRep_Nov||Stim_Type),
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)
>>>>>>> master
  
  # for contrast coding: when variable set to 0 = will be ignored 
  # intercept = mean of full data including variable which was set to 0
  # based on: https://pagepiccinini.com/2016/03/18/contrast-coding-with-three-level-variables/#toc_3
  
<<<<<<< HEAD
  contrasts(EEG_task_Acc_glmm$emot) = cbind(EvsN,HvsA)
  
  
# Build full model
  mod_Acc_EEG.glmm = glmer(Response ~ emot*rep + WM_scal +
                            (1|ID) +
=======
# ID   
  mod_Acc_EEG.glmm3 = glmer(Response ~ Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                            (1 |ID) +
                            (0 + Emo_Neu + Hap_Ang + Rep_Nov + Hap_AngxRep_Nov||Stim_Type),
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)

# Stim Type
  mod_Acc_EEG.glmm4 = glmer(Response ~ Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                            (1 + Hap_Ang + Rep_Nov ||ID) +
                            (1|Stim_Type),
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)
# Calculate ANOVAs
  anova(mod_Acc_EEG.glmm2,mod_Acc_EEG.glmm3)
  anova(mod_Acc_EEG.glmm2,mod_Acc_EEG.glmm4)


# Final model
  mod_Acc_EEG.glmm4 = glmer(Response ~ Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                            (1 + Hap_Ang + Rep_Nov ||ID) +
>>>>>>> master
                            (1|Stim_Type),
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)
          
```

<<<<<<< HEAD
 ``r format(formula(mod_Acc_EEG.glmm))``
=======
 ``r format(formula(mod_Acc_EEG.glmm4))``
>>>>>>> master
 
---

###### Overdispersion

If the p-value is < 0.05, data would be overdispersed. Here p > 0.05. Hence, overdispersion is not a problem.

```{r EEG_Acc_GLMM_overd_1, results = TRUE}

# Assumption check: Appropriate estimation of variance - check for overdispersion
<<<<<<< HEAD
  overdisp_fun(mod_Acc_EEG.glmm)
=======
  overdisp_fun(mod_Acc_EEG.glmm4)
>>>>>>> master
```

---


##### Reaction time LMM: {.tabset .tabset-pills}

###### Random effect structure

<!-- LMM model specifications -->

The final model was: 

<<<<<<< HEAD
```{r EEG_RT_LMM_build_res}

# Choose outlier-free data and correct answers    
  EEG_task_RT_lmm = subset(EEG_task_data,  Response == 1 & Exclude_smaller_250ms == FALSE)
=======
```{r EEG_RT_LMM1_build_res}

# Choose outlier-free data and correct answers    
  EEG_task_RT_lmm = subset(EEG_task_data,Exclude_smaller_250ms == FALSE 
                           & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE 
                           & EEG_trial_loss == 1)

  EEG_task_RT_lmm = subset(EEG_task_RT_lmm, Response == 1)
>>>>>>> master

# Define novel vs repeated trials
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 4]='c_happy';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 5]='c_neutral';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 6]='c_angry';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 7]='ic_happy';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 8]='ic_neutral';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 9]='ic_angry';

# Create one variable for emotion and one for repetition 
  EEG_task_RT_lmm$emot[(EEG_task_RT_lmm$Target == 'c_happy')  | (EEG_task_RT_lmm$Target == 'ic_happy')] = 1
  EEG_task_RT_lmm$emot[(EEG_task_RT_lmm$Target == 'c_angry')  | (EEG_task_RT_lmm$Target == 'ic_angry')] = 2
  EEG_task_RT_lmm$emot[(EEG_task_RT_lmm$Target == 'c_neutral')  | (EEG_task_RT_lmm$Target == 'ic_neutral')] = 3
  
  EEG_task_RT_lmm$rep[(EEG_task_RT_lmm$Target == 'c_happy')  | (EEG_task_RT_lmm$Target == 'c_angry') | (EEG_task_RT_lmm$Target == 'c_neutral')] = 1
  EEG_task_RT_lmm$rep[(EEG_task_RT_lmm$Target == 'ic_happy')  | (EEG_task_RT_lmm$Target == 'ic_angry') | (EEG_task_RT_lmm$Target == 'ic_neutral')] = 2

# Rename variables   
  EEG_task_RT_lmm$emot[EEG_task_RT_lmm$emot == 1]='happy';
  EEG_task_RT_lmm$emot[EEG_task_RT_lmm$emot == 2]='angry';
  EEG_task_RT_lmm$emot[EEG_task_RT_lmm$emot == 3]='neutral';
  EEG_task_RT_lmm$rep[EEG_task_RT_lmm$rep == 1]='repeated';
  EEG_task_RT_lmm$rep[EEG_task_RT_lmm$rep == 2]='novel';

# Factor variables
  EEG_task_RT_lmm$rep = factor(EEG_task_RT_lmm$rep)
  EEG_task_RT_lmm$emot = factor(EEG_task_RT_lmm$emot) 

# Create contrasts 
  contrasts(EEG_task_RT_lmm$emot) = contr.treatment(3,  base = 3)
<<<<<<< HEAD
  contrasts(EEG_task_RT_lmm$rep) = c(-0.5,0.5)

# A = angry, N = neutral, H = happy
  HvsA = c(0.5,-0.5,0) # compare: happy vs. angry
  EvsN = c(-0.25,-0.25,0.5) # compare happy/angry to neutral 
  contrasts(EEG_task_RT_lmm$emot) = cbind(EvsN,HvsA)
  
  mod_RT_EEG.lmer = lmer(log(RTs) ~ emot*rep + WM_scal +
                                   (1 |ID) +
                                   (1 |Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))
  
```

  ``r format(formula(mod_RT_EEG.lmer))``
=======
  contrasts(EEG_task_RT_lmm$rep) = contr.treatment(2,  base = 1)

# A = angry, N = neutral, H = happy
  HvsA = c(0.5,-0.5,0)
  EvsN = c(0.5,0.5,0)
  contrasts(EEG_task_RT_lmm$emot) = cbind(EvsN,HvsA)

# Add contrast columns
  mm_EEG_task_RT =  model.matrix( ~ emot*rep, EEG_task_RT_lmm)   

# Attach to dataframe
  EEG_task_RT_lmm[,(ncol(EEG_task_RT_lmm)+1):(ncol(EEG_task_RT_lmm)+6)] = mm_EEG_task_RT
  names(EEG_task_RT_lmm)[(ncol(EEG_task_RT_lmm)-5):ncol(EEG_task_RT_lmm)] = c("Mean","Emo_Neu", "Hap_Ang",
                                                                              "Rep_Nov", "Emo_NeuxRep_Nov",
                                                                              "Hap_AngxRep_Nov") 

# Build full model 
  mod_RT_EEG.lmer1 = lmer(log(RTs) ~ 
                                   Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                                   (1 + Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov||ID) +
                                   (1 + Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov||Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  

## PCA to check random effect structure (Cut-off: 0.005 - 0.001)

# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_RT_EEG.lmer1))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_RT_EEG.lmer1),comp = "Variance")

# 3rd: remove all terms with zero variance --> comprises final model 
  mod_RT_EEG.lmer2 = lmer(log(RTs) ~ 
                                   Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                                   (1 + Rep_Nov||ID) +
                                   (1 + Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov||Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  

# 4th: re-check the model PCA / variance of random factors
  summary(rePCA(mod_RT_EEG.lmer2))
  print(VarCorr(mod_RT_EEG.lmer2),comp = "Variance")

# 5th: Do Likelihood Ratio Test (LRT) - to check whether all random slopes improve the model

# LRT without random slope Nov_Rep for ID
  mod_RT_EEG.lmer3 = lmer(log(RTs) ~ 
                                   Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                                   (1 |ID) +
                                   (1 + Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov||Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  

# Calculate ANOVA
  anova(mod_RT_EEG.lmer2,mod_RT_EEG.lmer3)

# LRT without random slope Nov_Rep for Stim_Type
  mod_RT_EEG.lmer4 = lmer(log(RTs) ~ 
                                   Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                                   (1 + Rep_Nov||ID) +
                                   (1 |Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  
  
  
# LRT without random slope Nov_Rep for Stim_Type
  mod_RT_EEG.lmer2 = lmer(log(RTs) ~ 
                                   Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                                   (1 + Rep_Nov||ID),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  
  
  
# Calculate ANOVA
  anova(mod_RT_EEG.lmer2,mod_RT_EEG.lmer3)
  anova(mod_RT_EEG.lmer2,mod_RT_EEG.lmer4)


# 6th: remove random slopes which did not improve the model 
  mod_RT_EEG.lmer5 = lmer(log(RTs) ~ 
                                   Emo_Neu + Hap_Ang + Rep_Nov + Emo_NeuxRep_Nov + Hap_AngxRep_Nov + WM_scal +  
                                   (1 + Rep_Nov||ID),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  
  
```

  ``r format(formula(mod_RT_EEG.lmer5))``
>>>>>>> master

###### Normality of residuals 

RTs were log-transformed (determined using the Box-Cox procedure) to meet the assumption of normally distributed residuals.

```{r EEG_RT_LMM1_normres, fig.width = 6, fig.asp = .62}

## Check properties of DV / residuals 

# Visualize normality assumption of residuals (without log transform)
  mod_RT_lmm_no_log = lm(RTs ~ Cong, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_no_log = residuals(mod_RT_lmm_no_log)

  par(mfrow=c(1,2))
  qqpl_RT_lmm_no_log = qqPlot(res.mod_RT_lmm_no_log, main="QQplot before transformation")    
  norm_RT_lmm_no_log = plot(density(res.mod_RT_lmm_no_log), main="Density plot before transformation")  
  par(mfrow=c(1,1))

# Check which transformation of DV is suitable

# Calculate box-cox plot
  mod_RT_targ = lm(RTs ~ Cong, data=EEG_task_RT_lmm)
  boxcox(mod_RT_targ)   

# Visualize normality assumption of residuals (with log transform)
  mod_RT_lmm_log = lm(log(RTs) ~ Cong, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_log = residuals(mod_RT_lmm_log)
  
  par(mfrow=c(1,2))
  qqpl_RT_lmm_log = qqPlot(res.mod_RT_lmm_log, main="QQplot after transformation")    
  norm_RT_lmm_log = plot(density(res.mod_RT_lmm_log), main="Density plot after transformation")  
  par(mfrow=c(1,1))
          
```

---

###### Homoscedasticity 

We assume homoscedasticity based on visual inspection. 

```{r EEG_RT_LMM1_homosk, fig.width = 5, fig.asp = .62}

# Check homoscedasticity
  plot(fitted(mod_RT_EEG.lmer), residuals(mod_RT_EEG.lmer))
  abline(0, 0) 
```    

---

#### **Results**

```{r EEG_task_post_hoc_calc, results = "asis"}

<<<<<<< HEAD
### Reaction time

# Calculate post-hoc tests
  EEG_task_RT_lmm$interaction = interaction(EEG_task_RT_lmm$rep, EEG_task_RT_lmm$emot)

  mod_RT_EEG.lmer_model =   lmer(log(RTs) ~ interaction + WM_scal +
                                   (1 |ID) +
                                   (1 |Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))
  
# Choose contrasts of interest / add fdr-correction
  
  
# Choose contrasts of interest / add fdr-correction
  mod_RT_EEG.lmer_model_posthoc =  summary(glht(mod_RT_EEG.lmer_model, linfct=mcp(interaction = c(
                                                        "repeated.neutral - repeated.angry = 0",
                                                        "novel.neutral - novel.angry = 0",
                                                        "novel.neutral - novel.happy = 0",
                                                        "repeated.neutral - repeated.happy = 0")), test = adjusted(type = "fdr")))
  
# Get ready for presentation in RMarkdown
  tab1 = merge(as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$coefficients),as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$sigma),by=0)
  tab2 = as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$pvalues)
  rownames(tab2) = rownames(as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$tstat))
  tab2 = merge(as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$tstat),tab2,by=0)
  post_hoc_tests_EEG_RT = merge(tab1,tab2,by='Row.names')
  colnames(post_hoc_tests_EEG_RT) = c("Contrast","Est.","Std. Error", "z value", "p value")

  
```

There were no accuracy differences for facial expression contrasts (emotional vs. neutral expressions: $\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm))[3,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm))[3,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm))[3,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[3,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[3,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[3,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[3,1]))[3])`]; happy vs. angry expressions: $\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm))[4,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm))[4,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm))[4,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[4,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[4,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[4,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[4,1]))[3])`]) or repetition ($\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm))[2,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm))[2,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm))[2,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[2,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[2,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[2,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[2,1]))[3])`]). Interactions between facial expression contrasts and repetition yielded no significant results (emotional vs. neutral facial expressions: $\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm))[6,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm))[6,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm))[6,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[6,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[6,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[6,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[6,1]))[3])`]; happy vs. angry expressions: $\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm))[7,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm))[7,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm))[7,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[7,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[7,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm))[7,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm))[7,1]))[3])`]). For reaction times, the emotional vs. neutral facial expression contrast yielded no significant results ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer))[3,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer))[3,5])`). In line with our hypothesis, happy faces were detected faster than angry faces ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer))[4,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer))[4,5])`). The main effect for repetition was not significant ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer))[2,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer))[2,5])`). The interaction of emotional vs. neutral expressions with repetition, however, was significant ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer))[6,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer))[6,5])`). Novel happy faces were detected faster than novel neutral faces (`r reportP(post_hoc_tests_EEG_RT[2,5])`). None of the other post-hoc tests were significant (all *p* > `r reportci(post_hoc_tests_EEG_RT[3,5])`). Similarly, the interaction of happy vs. angry expressions with repetition was not significant ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer))[7,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer))[7,5])`).
 
<div align="center">

```{r EEG_Acc_RT_GLMM_results, results = 'asis'}

# Create labels
  labels = c("Emotion vs. Neutral", "Happy vs. Angry", "Repetition", "Working Memory", "E vs. N x Repetition ", "H vs. A x Repetition")

# Create table
  tab_model(mod_Acc_EEG.glmm, mod_RT_EEG.lmer, show.intercept = FALSE,
          pred.labels= labels, show.ci = FALSE,
          show.se = TRUE, string.se = "SE",
          show.stat = TRUE, string.stat = "t",
          show.re.var = TRUE, show.obs = FALSE,
          emph.p = TRUE, dv.labels=c("Accuracy", "Reaction time") , show.icc = TRUE)
  
```

</div>

<br>

*Note:* p-values for the fixed effects calculated using Wald-statistics approximation, uncorrected. *SE*: standard error; *t*: test statistic coefficient; *p*: p-value; *σ2*: within-group variance; *τ00*: between-group variance; *ICC*: interclass correlation (ratio of between-cluster variance to total variance); *N*: number of random effects. 

<br>

**Post-hoc tests for Reaction time: Repetition with emotional vs. neutral facial expressions contrast**
=======
### Accuracy

# Calculate post-hoc tests
  EEG_task_Acc_glmm$interaction = interaction(EEG_task_Acc_glmm$rep, EEG_task_Acc_glmm$emot)
 
  EEG_task_Acc_glmm_model =  glmer(Response ~ interaction + WM_scal +  
                            (1 + Hap_Ang + Rep_Nov ||ID) +
                            (1|Stim_Type),
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)
  
# Choose contrasts of interest / add fdr-correction
  EEG_task_Acc_glmm_model_posthoc =  summary(glht(EEG_task_Acc_glmm_model, linfct=mcp(interaction = c(
                                                        "repeated.neutral - repeated.angry = 0",
                                                        "novel.neutral - novel.angry = 0",
                                                        "novel.neutral - novel.happy = 0",
                                                        "repeated.neutral - repeated.happy = 0")), test = adjusted(type = "fdr")))
 
# Get ready for presentation in RMarkdown
  tab1 = merge(as.data.frame(EEG_task_Acc_glmm_model_posthoc$test$coefficients),as.data.frame(EEG_task_Acc_glmm_model_posthoc$test$sigma),by=0)
  tab2 = as.data.frame(EEG_task_Acc_glmm_model_posthoc$test$pvalues)
  rownames(tab2) = rownames(as.data.frame(EEG_task_Acc_glmm_model_posthoc$test$tstat))
  tab2 = merge(as.data.frame(EEG_task_Acc_glmm_model_posthoc$test$tstat),tab2,by=0)
  post_hoc_tests_EEG_acc = merge(tab1,tab2,by='Row.names')
  colnames(post_hoc_tests_EEG_acc) = c("Contrast","Est.","Std. Error", "z value", "p value")

### RTs  
  
# Calculate post-hoc tests
  EEG_task_RT_lmm_model =   lmer(log(RTs) ~ 
                                   emot*rep+ WM_scal +  
                                   (1 + Rep_Nov||ID) +
                                   (1 |Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))  
  
# Choose contrasts of interest / add fdr-correction
  EEG_task_RT_lmm_model_posthoc =  summary(glht(EEG_task_RT_lmm_model, linfct=mcp(emot = c(
                                                        "neutral - happy = 0",
                                                        "neutral - angry = 0")), test = adjusted(type = "fdr")))
 
 
# Get ready for presentation in RMarkdown
  tab1 = merge(as.data.frame(EEG_task_RT_lmm_model_posthoc$test$coefficients),as.data.frame(EEG_task_RT_lmm_model_posthoc$test$sigma),by=0)
  tab2 = as.data.frame(EEG_task_RT_lmm_model_posthoc$test$pvalues)
  rownames(tab2) = rownames(as.data.frame(EEG_task_RT_lmm_model_posthoc$test$tstat))
  tab2 = merge(as.data.frame(EEG_task_RT_lmm_model_posthoc$test$tstat),tab2,by=0)
  post_hoc_tests_EEG_RT = merge(tab1,tab2,by='Row.names')
  colnames(post_hoc_tests_EEG_RT) = c("Contrast","Est.","Std. Error", "z value", "p value")  
  
```

We found larger accuracy rates for emotional vs. neutral facial expressions ($\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm4))[2,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm4))[2,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm4))[2,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[2,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[2,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[2,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[2,1]))[3])`]), but no accuracy differences for happy vs. angry facial expressions ($\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm4))[3,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm4))[3,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm4))[3,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[3,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[3,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[3,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[3,1]))[3])`]). There was no main effect of repetition ($\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm4))[4,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm4))[4,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm4))[4,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[4,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[4,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[4,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[4,1]))[3])`]). Instead, the emotional vs. neutral facial expression contrast was qualified by an interaction with repetition ($\beta$ `r reportbe(coef(summary(mod_Acc_EEG.glmm4))[5,1])`, `r reportP(coef(summary(mod_Acc_EEG.glmm4))[5,4])`, *OR* `r reportbe(exp(coef(summary(mod_Acc_EEG.glmm4))[5,1]))` [95% CI: `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[5,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[4,1]))[1])`, `r reportci((exp(coef(summary(mod_Acc_EEG.glmm4))[5,1]) + qnorm(c(0.05,0.5,0.95)) * exp(coef(summary(mod_Acc_EEG.glmm4))[5,1]))[3])`]). Post-hoc tests indicated that children were more accurate when Face 2 yielded a novel happy compared to a novel neutral facial expression (`r reportP(post_hoc_tests_EEG_acc[2,5])`). None of the other post-hoc tests reached significance (all > `r post_hoc_tests_EEG_acc[order(post_hoc_tests_EEG_acc[,5]) == 2,5]`).

   Regarding reaction times, the emotional vs. neutral facial expression contrast was significant ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer5))[2,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer5))[2,5])`), however, none of the post-hoc tests indicated significant differences (happy vs. neutral: `r reportP(post_hoc_tests_EEG_RT[2,5])`; angry vs. neutral: `r reportP(post_hoc_tests_EEG_RT[1,5])`). We detected no reaction time differences between happy vs. angry facial expressions ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer5))[3,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer5))[3,5])`). Neither the main effect of repetition ($\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer5))[4,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer5))[4,5])`), nor its interaction with the facial expression contrasts (emotional vs. neutral: $\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer5))[5,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer5))[5,5])`; angry vs. happy: $\beta$ `r reportbe(coef(summary(mod_RT_EEG.lmer5))[6,1])`, `r reportP(coef(summary(mod_RT_EEG.lmer5))[6,5])`) was significant. 

<div align="center">

```{r EEG_Acc_RT_GLMM_results, results = 'asis'}

# Create labels
  labels = c("Emotion vs. Neutral", "Happy vs. Angry", "Repetition", "Repetition x E vs. N", "Repetition x H vs. A", "Working Memory")

# Create table
  tab_model(mod_Acc_EEG.glmm4, mod_RT_EEG.lmer5, show.intercept = FALSE,
          pred.labels=labels, show.ci = FALSE,
          show.se = TRUE, string.se = "SE",
          show.stat = TRUE, string.stat = "t",
          show.re.var = TRUE, show.obs = FALSE,
          emph.p = TRUE, dv.labels=c("Accuracy", "Reaction time") , show.icc = TRUE)
  
```

</div>

<br>

*Note:* p-values for the fixed effects calculated using Wald-statistics approximation, uncorrected. *SE*: standard error; *t*: test statistic coefficient; *p*: p-value; *σ2*: within-group variance; *τ00*: between-group variance; *ICC*: interclass correlation (ratio of between-cluster variance to total variance); *N*: number of random effects. 

<br>

**Post-hoc tests for Accuracy: Repetition x E vs. N contrast** 

```{r EEG_Acc_post_hoc, results = "asis"}
  
# Create table
  kable(post_hoc_tests_EEG_acc) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)
  
```

<br>

**Post-hoc tests for Reaction time: Emotional vs. Neutral faces contrast**
>>>>>>> master

```{r EEG_RT_post_hoc, results = "asis"}

# Create table
  kable(post_hoc_tests_EEG_RT) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)  

```

```{r save_models, include = FALSE, eval = FALSE}

# Save data set in RData format
<<<<<<< HEAD
  save(mod_Acc_EEG.glmm, file = "./data/mod_Acc_EEG.glmm.RData")
  save(mod_RT_EEG.lmer, file = "./data/mod_RT_EEG.lmer.RData")

=======
  save(mod_Acc_EEG.glmm4, file = "./data/mod_Acc_EEG.glmm4.RData")
  save(mod_RT_EEG.lmer5, file = "./data/mod_RT_EEG.lmer5.RData")
  
  save(post_hoc_tests_EEG_acc, file = "./data/post_hoc_tests_EEG_acc.RData")
>>>>>>> master
  save(post_hoc_tests_EEG_RT, file = "./data/post_hoc_tests_EEG_RT.RData")
    
```

# Session info

<!-- Provide session info  -->

```{r session_info, results = TRUE}

# Get session info 
  sessionInfo()

```

