---
title: "Matching task"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  options(max.print="75")

  knitr::opts_chunk$set(echo=TRUE,
  	             #cache=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE,
  	             fig.align="center",
  	             fig.width=6, fig.height=4)
  knitr::opts_knit$set(width=75)
  
# Swipe environment
  rm(list=ls())
  
# Set libraries
  library(cowplot)
  library(dplyr)
  library(eeptools)
  library(EnvStats)
  library(ez)
  library(ggplot2)
  library(ggstatsplot)
  library(Hmisc)
  library(lme4)
  library(lmerTest)
  library(MASS)
  library(miceadds)
  library(psych)
  library(reshape2)
  library(Rmisc)
  library(sjPlot)
  library(sjmisc)
  library(sjlabelled)
  library(tidyverse)

# Load overdispersion function
  overdisp_fun = function(model) {
    rdf = df.residual(model)
    rp = residuals(model,type="pearson")
    Pearson.chisq = sum(rp^2)
    prat = Pearson.chisq/rdf
    pval = pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
  }
  
# Raincloud plot function   
  source("./functions/geom_flat_violin.R")
  
# Round to 2 digits   
  options(digits=2)
  
# Disable scientific notation in R
  options(scipen = 999)
  
# Set figure theme  
  theme_SN = theme(axis.title.y = element_text(size = 15, margin = margin(t = 0, r = 20, b = 0, l = 0)),
          panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "black", linetype = "dotted", size=0.6),
          panel.grid.minor.y = element_blank(),
          panel.background = element_rect(colour = "black", size = 0.5),
          text=element_text(size = 15),
          legend.position = "none")
  
# Set figure color palettes
  emotion_col = c("#829dac","#1d4f6a","#032f47")
  nov_col = c("#547460","#0A381C")
  
```

<!-- Load data set-->

```{r load_data, include = FALSE}

# Load EEG task data
  load.Rdata(filename="./data/EEG_task_data.Rdata", "EEG_task_data")
  
```

# Task description

Our EEG paradigm included a delayed same-different matching task in which children had do indicate whether Face 1 and Face 2 showed the same (`repeated`) or a different emotional facial expression (`novel`). We measured participants' accuracy rates and reaction times. 

We excluded: 

  + Reaction times < 250 ms or >  7s
  + Values </> 2.5 of the median absolute deviation (MAD) based on the individual participant
  + Incorrect answers
  + Rejected EEG trials
  
We calculated general linear mixed models (GLMM) for accuracy rates and linear mixed models (LMM) for reaction times. Fixed effects are defined for each model individually. Chronological age and working memory were entered as scaled covariates in all (general) linear mixed model analyses to control for cognitive abilities of the children as well as potential differences in age.

The random effects structure included random intercepts for participants `(1|ID)` and stimulus `(1|Stim_Type)`. For each model, we commenced with the maximal random effect structure. Random intercepts were defined for participants and stimuli. Random slopes were defined for all predictors, but not covariates. We set correlations of random terms to zero and performed a principal component analysis on the random-effects variance-covariance estimates to determine the number of components supported by the data. We removed random effects explaining zero variance, in order to prevent over-parametrization. Afterwards, we checked whether all random intercepts improved the model using likelihood-ratio-testing.

# Accuracy

We predicted that children would be less accurate when Face 1 and Face 2 were repeated (`GLMM 1`). We also expected the highest accuracy rates for pairings where happy faces were involved (`GLMM 2`). 

<br>

#### **Descriptive statistics** 

<!-- Draw EEG task accuracy plots -->

```{r EEG_Acc_plots, results = TRUE}

# Select outlier-free data and correct trials
  EEG_task_Acc_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)
  EEG_task_Acc_plot = subset(EEG_task_Acc_plot, Response == 1)

## Plot separated by novel vs repeated trials  
  
# Recode variable
  EEG_task_Acc_plot$Cong[EEG_task_Acc_plot$Cong == 1] = "repeated"
  EEG_task_Acc_plot$Cong[EEG_task_Acc_plot$Cong == 2] = "novel"

# Get accuracy for novel and repeated condition
  acc_all = data.frame(xtabs(~ID+Cong, EEG_task_Acc_plot))

# Recode to accuracy in percent (72 novel trials, 72 repeated trials)
  acc_all$Freq = (acc_all$Freq/72)*100

# Factor condition
  acc_all$Cong = as.factor(acc_all$Cong)

# Calculate descriptives on accuracy
  stats_acc_all = summarySE(acc_all, measurevar="Freq", groupvars=c("Cong"))

# Plot accuracy
  EEG_acc_plot=ggplot(stats_acc_all, aes(x=Cong, y=Freq, fill = Cong)) +
    geom_bar(position=position_dodge(), stat="identity",colour="black", size=0.7,width=0.9) +
    geom_errorbar(aes(ymin=Freq-se, ymax=Freq+se), size=1, width=0.2, position=position_dodge(.9)) +
    labs (x= "", y = "Accuracy [%]") +
    scale_fill_manual(values=nov_col)+
    coord_cartesian(ylim = c(0, 65)) +
    scale_y_continuous(breaks=seq(0,60,20))+
    theme_bw()+
    theme_SN

## Plot separated by emotions

# Select outlier-free data and correct trials
  EEG_task_Acc_targ_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)
  EEG_task_Acc_targ_plot = subset(EEG_task_Acc_targ_plot,Response == 1)
  
# Recode variable
  EEG_task_Acc_targ_plot$Target[EEG_task_Acc_targ_plot$Target==4] = "happy"
  EEG_task_Acc_targ_plot$Target[EEG_task_Acc_targ_plot$Target==5] = "neutral"
  EEG_task_Acc_targ_plot$Target[EEG_task_Acc_targ_plot$Target==6] = "angry"
  
  EEG_task_Acc_targ_plot$Target[EEG_task_Acc_targ_plot$Target==7] = "happy"
  EEG_task_Acc_targ_plot$Target[EEG_task_Acc_targ_plot$Target==8] = "neutral"
  EEG_task_Acc_targ_plot$Target[EEG_task_Acc_targ_plot$Target==9] = "angry"
  
  EEG_task_Acc_targ_plot$Target = factor(EEG_task_Acc_targ_plot$Target, levels=c("neutral","happy","angry"))
  
# Get accuracy for novel and repeated condition
  acc_emo = data.frame(xtabs(~ID+Target, EEG_task_Acc_targ_plot))
  
# Recode to accuracy in percent (48 happy trials, 49 neutral trials, 47 angry trials)
  acc_emo$Freq[acc_emo$Target== "happy"] = (acc_emo$Freq[acc_emo$Target== "happy"]/48)*100
  acc_emo$Freq[acc_emo$Target== "neutral"] = (acc_emo$Freq[acc_emo$Target== "neutral"]/49)*100
  acc_emo$Freq[acc_emo$Target== "angry"] = (acc_emo$Freq[acc_emo$Target== "angry"]/47)*100
  
# Factor condition
  acc_emo$Target = as.factor(acc_emo$Target)
  
# Calculate descriptives on accuracy
  stats_acc_emo = summarySE(acc_emo, measurevar="Freq", groupvars=c("Target"))
  
# Plot accuracy
  EEG_acc_emo_plot=ggplot(stats_acc_emo, aes(x=Target, y=Freq, fill = Target)) +
    geom_bar(position=position_dodge(), stat="identity",colour="black", size=0.7,width=0.9) +
    geom_errorbar(aes(ymin=Freq-se, ymax=Freq+se), size=1, width=0.2, position=position_dodge(.9)) +
    labs (x = "", y = "Accuracy [%]") +
    coord_cartesian(ylim = c(0, 65)) +
    scale_y_continuous(breaks=seq(0,60,20))+
    scale_fill_manual(values=emotion_col)+
    theme_bw()+
    theme_SN+
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank())

# Display plots
  fig_EEG_acc = cowplot::plot_grid(EEG_acc_plot, EEG_acc_emo_plot, ncol=2, rel_widths=c(1, 1))
  fig_EEG_acc  

```

#### **Model specification** {.tabset .tabset-pills}

<!-- GLMM model specifications -->

<br>

##### GLMM 1: Random effect structure 

```{r EEG_Acc_GLMM_res_1}

# Select outlier-free data
  EEG_task_Acc_glmm = subset(EEG_task_data,Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)

# Factor random effects
  EEG_task_Acc_glmm$ID = as.factor(EEG_task_Acc_glmm$ID)
  EEG_task_Acc_glmm$Stim_Type = as.factor(EEG_task_Acc_glmm$Stim_Type)

# Factor fixed factor congruency
  EEG_task_Acc_glmm$Cong[EEG_task_Acc_glmm$Cong==1] = "repeated"
  EEG_task_Acc_glmm$Cong[EEG_task_Acc_glmm$Cong==2] = "novel"
  EEG_task_Acc_glmm$Cong = factor(EEG_task_Acc_glmm$Cong)

# Set effect coding contrast
  contrasts(EEG_task_Acc_glmm$Cong) = contr.sum(2)/2

## Construct full model

# Create contrast matrix
  mm_EEG_task_Acc =  model.matrix( ~ Cong, EEG_task_Acc_glmm)

# Attach to dataframe
  EEG_task_Acc_glmm = EEG_task_Acc_glmm
  EEG_task_Acc_glmm[,(ncol(EEG_task_Acc_glmm)+1):(ncol(EEG_task_Acc_glmm)+2)] = mm_EEG_task_Acc
  names(EEG_task_Acc_glmm)[(ncol(EEG_task_Acc_glmm)-1):ncol(EEG_task_Acc_glmm)] = c("Grand Mean", "Nov_Rep")

# Build full model
  mod_Acc_EEG.glmm1 = glmer(Response ~ Nov_Rep + scale(Age) + scale(WM) +
                              (1 + Nov_Rep||ID) +
                              (1 + Nov_Rep||Stim_Type),
                              data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                              family = binomial)

## Check random effect structure (cut-off: 0.005 - 0.001)

# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_Acc_EEG.glmm1))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_Acc_EEG.glmm1),comp = "Variance")
  

# Adapt model
  mod_Acc_EEG.glmm2 = glmer(Response ~ Nov_Rep + scale(Age) + scale(WM) +
                              (1 + Nov_Rep||ID) +
                              (0 + Nov_Rep||Stim_Type),
                              data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                              family = binomial)
  
# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_Acc_EEG.glmm2))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_Acc_EEG.glmm2),comp = "Variance")

## Likelihood-ratio-testing
  
# ID   
  mod_Acc_EEG.glmm3 = glmer(Response ~ Nov_Rep + scale(Age) + scale(WM) +
                              (1 |ID) +
                              (0 + Nov_Rep||Stim_Type),
                              data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                              family = binomial)

# Stim Type
 mod_Acc_EEG.glmm4 = glmer(Response ~ Nov_Rep + scale(Age) + scale(WM) +
                              (1 + Nov_Rep||ID) +
                              (1|Stim_Type),
                              data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                              family = binomial)

# Calculate ANOVAs
  anov_glmm1_glmm2_3 = anova(mod_Acc_EEG.glmm2,mod_Acc_EEG.glmm3)
  anov_glmm1_glmm2_4 = anova(mod_Acc_EEG.glmm2,mod_Acc_EEG.glmm4)


# Final model
  mod_Acc_EEG.glmm4 = glmer(Response ~ Nov_Rep + scale(Age) + scale(WM) +
                            (1 + Nov_Rep||ID) +
                            (1 | Stim_Type),
                          data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                          family = binomial)
          
```

According to our hypothesis, the main fixed effects of interest was novelty of Face 2. We applied a scaled sum contrast to compare trials with novel vs repeated emotions (`Novel vs Repeated`). Consequently, we fitted single-trial data to the following model:

 ``r format(formula(mod_Acc_EEG.glmm4))``

---

##### GLMM 1: Overdispersion

If the p-value is < 0.05, data would be overdispersed. Here p > 0.05. Hence, overdispersion is not a problem.

```{r EEG_Acc_GLMM_overd_1, results = TRUE}

# Assumption check: Appropriate estimation of variance - check for overdispersion
  overdisp_fun(mod_Acc_EEG.glmm4)

```

---

##### GLMM 2: Random effect structure 

```{r EEG_Acc_GLMM_res_2}

# Get outlier-free data
  EEG_task_Acc_targ_glmm = subset(EEG_task_data, Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)

# Rename variables
  EEG_task_Acc_targ_glmm$Target[EEG_task_Acc_targ_glmm$Target==4] = "hap"
  EEG_task_Acc_targ_glmm$Target[EEG_task_Acc_targ_glmm$Target==5] = "neu"
  EEG_task_Acc_targ_glmm$Target[EEG_task_Acc_targ_glmm$Target==6] = "ang"
  
  EEG_task_Acc_targ_glmm$Target[EEG_task_Acc_targ_glmm$Target==7] = "hap"
  EEG_task_Acc_targ_glmm$Target[EEG_task_Acc_targ_glmm$Target==8] = "neu"
  EEG_task_Acc_targ_glmm$Target[EEG_task_Acc_targ_glmm$Target==9] = "ang"

# Create factor, get neutral as baseline
  EEG_task_Acc_targ_glmm$Target = factor(EEG_task_Acc_targ_glmm$Target, levels=c("neu","hap","ang"))
  EEG_task_Acc_targ_glmm$ID = as.factor(EEG_task_Acc_targ_glmm$ID)
  EEG_task_Acc_targ_glmm$Stim_Type = as.factor(EEG_task_Acc_targ_glmm$Stim_Type)

# Set treatment contrast
  contrasts(EEG_task_Acc_targ_glmm$Target) = contr.treatment(3)

## Construct full model

# Add contrast columns
  mm_EEG_task_Acc_targ =  model.matrix( ~ Target, EEG_task_Acc_targ_glmm)

# Attach to dataframe
  EEG_task_Acc_targ_glmm[,(ncol(EEG_task_Acc_targ_glmm)+1):(ncol(EEG_task_Acc_targ_glmm)+3)] = mm_EEG_task_Acc_targ
  names(EEG_task_Acc_targ_glmm)[(ncol(EEG_task_Acc_targ_glmm)-2):ncol(EEG_task_Acc_targ_glmm)] = c("Mean","Neu_Hap", "Neu_Ang")

# Build full model
  mod_Acc_targ.glmm1 = glmer(Response ~ Neu_Hap + Neu_Ang + scale(Age) + scale(WM)
                             + (1 + Neu_Hap + Neu_Ang||ID)
                             + (1 + Neu_Hap + Neu_Ang||Stim_Type),
                             data = EEG_task_Acc_targ_glmm,
                             control=glmerControl(calc.derivs = FALSE),
                             family = binomial)

## Check random effect structure (cut-off: 0.005 - 0.001)

# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_Acc_targ.glmm1))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_Acc_targ.glmm1),comp = "Variance")


# Re-build model
  mod_Acc_targ.glmm2 = glmer(Response ~ Neu_Hap + Neu_Ang + scale(Age) + scale(WM)
                           + (1 + Neu_Ang||ID)
                           + (0 + Neu_Hap + Neu_Ang||Stim_Type),
                           data = EEG_task_Acc_targ_glmm,
                           control=glmerControl(calc.derivs = FALSE),
                           family = binomial)


# Re-check random structure
  summary(rePCA(mod_Acc_targ.glmm2))
  print(VarCorr(mod_Acc_targ.glmm2),comp = "Variance")


## Likelihood-ratio testing

# ID
  mod_Acc_targ.glmm3 = glmer(Response ~ Neu_Hap + Neu_Ang + scale(Age) + scale(WM)
                             + (1 |ID)
                             + (0 + Neu_Hap + Neu_Ang||Stim_Type),
                             data = EEG_task_Acc_targ_glmm,
                             control=glmerControl(calc.derivs = FALSE),
                             family = binomial)
# Stimulus type  
  mod_Acc_targ.glmm4 = glmer(Response ~ Neu_Hap + Neu_Ang + scale(Age) + scale(WM)
                             + (1 + Neu_Ang||ID)
                             + (1|Stim_Type),
                             data = EEG_task_Acc_targ_glmm,
                             control=glmerControl(calc.derivs = FALSE),
                             family = binomial)

# Calculate ANOVAs
  anov_glmm2_glmm3 = anova(mod_Acc_targ.glmm2,mod_Acc_targ.glmm3)
  anov_glmm2_glmm4 = anova(mod_Acc_targ.glmm2,mod_Acc_targ.glmm4)


# Final model
  mod_Acc_targ.glmm5 = glmer(Response ~ Neu_Hap + Neu_Ang + scale(Age) + scale(WM)
                             + (1 |ID)
                             + (0 + Neu_Hap + Neu_Ang||Stim_Type),
                             data = EEG_task_Acc_targ_glmm,
                             control=glmerControl(calc.derivs = FALSE),
                             family = binomial)
```

According to our hypothesis, the main fixed effects of interest was emotion of Face 2. We applied a treatment contrast comparing neutral vs happy and neutral vs angry emotional facial expressions (` Neutral vs Happy`, `Neutral vs Angry`). The final model was comprised of: 

  ``r format(formula(mod_Acc_targ.glmm5))``

---

##### GLMM 2: Overdispersion

If the p-value is < 0.05, data would be overdispersed. Here p > 0.05. Hence, overdispersion is not a problem.

```{r EEG_Acc_GLMM_overd_2, results = TRUE}

# Assumption check: Appropriate estimation of variance - check for overdispersion
  overdisp_fun(mod_Acc_targ.glmm5)

```
---

#### **Results**

<!-- Print GLMM results -->

Model results indicated that participants were equally accurate in trials with repeated in comparison to a novel emotion at Face 2. Descriptively, participants showed the highest accuracy when happy faces were presented as Face 2. This difference, however, was not significant in comparison to neutral faces. Similarly, there was no significant difference between angry and neutral facial expressions. 

<div align="center">

```{r EEG_Acc_GLMM_results, results = 'asis'}

# Create labels
  labels = c("Novel vs Repeated","Age","Working memory", "Neutral vs Happy", "Neutral vs Angry")

# Create table
  tab_model(mod_Acc_EEG.glmm4, mod_Acc_targ.glmm5,
          show.intercept = FALSE,
          pred.labels=labels, show.ci = FALSE,
          show.se = TRUE, string.se = "SE",
          show.stat = TRUE, string.stat = "t",
          show.re.var = TRUE, show.obs = FALSE,
          emph.p = TRUE, dv.labels=c("Face 2 Novelty","Face 2 Emotion") , show.icc = TRUE)
    
```

</div>

<br>

*Note:* p-values for the fixed effects calculated using Wald-statistics approximation, uncorrected. *SE*: standard error; *t*: test statistic coefficient; *p*: p-value; *σ2*: within-group variance; *τ00*: between-group variance; *ICC*: interclass correlation (ratio of between-cluster variance to total variance); *N*: number of random effects. 

# Reaction time

We expected children to be slower when Face 1 and Face 2 showed the same emotion (`LMM1`). Additionally, we expected the lowest reaction times for pairings where happy faces were involved (`LMM2`). Assumptions for multiple regression were checked for all models (normality of the residuals, linearity, multicollinearity, homoscedasticity). 

<br>

#### **Descriptives**

<!-- Draw EEG task RT plots -->

```{r EEG_RT_plots, results = TRUE}

## Plot separated by novel vs repeated trials 

# Choose outlier-free and correct trial data
  EEG_task_RT_plot = subset(EEG_task_data,Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)  
  EEG_task_RT_plot = subset(EEG_task_RT_plot, Response == 1)

# Rename values for repeated and novel trials 
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==1] = "repeated"
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==2] = "novel"
  
# Calculate summary
  lb = function(x) mean(x) - sd(x)
  ub = function(x) mean(x) + sd(x)
  
  sumld = ddply(EEG_task_RT_plot , ~ Cong, summarise,
                mean = mean(RTs), median = median(RTs), lower = lb(RTs), upper = ub(RTs))

# Plot rainclouds
  EEG_task_RT_rain = ggplot(data = EEG_task_RT_plot, aes(y = RTs, x = Cong, fill = Cong))  +
    geom_flat_violin(position = position_nudge(x = .18, y = 0),  adjust=1.5, trim=TRUE, alpha = 1, color="black") +
    geom_point(aes(y = RTs, color = Cong), shape = 19, position = position_jitter(width = .1), size = .7, alpha = 1) +
    geom_point(data = sumld, aes(x = Cong, y = mean), position = position_nudge(x = .22), size = 2.5) +
    geom_errorbar(data = sumld, aes(ymin = lower, ymax = upper, y = mean), position = position_nudge(x = .22), width = 0)+
    scale_y_continuous(name="Reaction time [ms]", breaks=seq(0,7000,2000), limits=c(250,7000))+
    scale_x_discrete(name="")+
    expand_limits(x =1, y = 1) +
    guides(fill = FALSE, color = FALSE) +
    coord_flip() + # flip or not?
    scale_fill_manual(values=nov_col) +
    scale_color_manual(values=nov_col)+
    theme_bw()+
    theme_SN +
    theme(panel.grid.major.y = element_blank())

## Plot separated by emotions

# Choose outlier-free and correct trial data
  EEG_task_RT_targ_plot = subset(EEG_task_data,Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE)
  EEG_task_RT_targ_plot = subset(EEG_task_RT_targ_plot, Response == 1)

# Choose EEG task data with correct trials
  EEG_task_RT_targ_plot = subset(EEG_task_RT_targ_plot, Response == 1)

# Rename variables
  EEG_task_RT_targ_plot$Target[EEG_task_RT_targ_plot$Target==4] = "happy"
  EEG_task_RT_targ_plot$Target[EEG_task_RT_targ_plot$Target==5] = "neutral"
  EEG_task_RT_targ_plot$Target[EEG_task_RT_targ_plot$Target==6] = "angry"
  EEG_task_RT_targ_plot$Target[EEG_task_RT_targ_plot$Target==7] = "happy"
  EEG_task_RT_targ_plot$Target[EEG_task_RT_targ_plot$Target==8] = "neutral"
  EEG_task_RT_targ_plot$Target[EEG_task_RT_targ_plot$Target==9] = "angry"

# Set target as factor / Recode target
  EEG_task_RT_targ_plot$Target = factor(EEG_task_RT_targ_plot$Target, levels=c("neutral","happy","angry"))

# Create summary  
  sumld = ddply(EEG_task_RT_targ_plot , ~ Target, summarise,
                mean = mean(RTs), median = median(RTs), lower = lb(RTs), upper = ub(RTs))

# Plot rainclouds
  EEG_RT_emo_rain = ggplot(data = EEG_task_RT_targ_plot, aes(y = RTs, x = Target, fill = Target))  +
    geom_point(aes(y = RTs, color = Target), shape = 19, position = position_jitter(width = .1), size = .7, alpha = 1) +
    geom_flat_violin(position = position_nudge(x = .18, y = 0),  adjust=1.5, trim=TRUE, alpha= 1, color="black") +
    geom_point(data = sumld, aes(x = Target, y = mean), position = position_nudge(x = .22), size = 2.5) +
    geom_errorbar(data = sumld, aes(ymin = lower, ymax = upper, y = mean), position = position_nudge(x = .22), width = 0)+
    scale_y_continuous(name="Reaction time [ms]", breaks=seq(0,7000,2000), limits=c(250,7000))+
    xlab("")+
    expand_limits(x = 1.00, y = 1) +
    guides(fill = FALSE, color = FALSE) +
    coord_flip() + # flip or not?
    scale_fill_manual(values=emotion_col) +
    scale_color_manual(values=emotion_col)+
    theme_bw()+
    theme_SN +
    theme(panel.grid.major.y = element_blank())
  
# Display plots
  fig_EEG_RT = cowplot::plot_grid(EEG_task_RT_rain, EEG_RT_emo_rain, ncol=2, rel_widths=c(1, 1))
  fig_EEG_RT

```
<br>

#### **Model specification** {.tabset .tabset-pills}

<!-- LMM assumption checks -->

##### LMM1: Random effect structure

```{r EEG_RT_LMM1_build_res}

# Choose outlier-free data and correct answers    
  EEG_task_RT_lmm = subset(EEG_task_data,Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)  
  EEG_task_RT_lmm = subset(EEG_task_RT_lmm, Response == 1)

# Recode for repeated and novel trials
  EEG_task_RT_lmm$Cong[EEG_task_RT_lmm$Cong==1] = "repeated"
  EEG_task_RT_lmm$Cong[EEG_task_RT_lmm$Cong==2] = "novel"

# Prepare fixed factors 
  EEG_task_RT_lmm$Cong = factor(EEG_task_RT_lmm$Cong)

# Factor ID and stimulus type 
  EEG_task_RT_lmm$Stim_Type = factor(EEG_task_RT_lmm$Stim_Type)
  EEG_task_RT_lmm$ID = factor(EEG_task_RT_lmm$ID)

# Define effect coding contrast for novelty 
  contrasts(EEG_task_RT_lmm$Cong) = contr.sum(2)/2

# Create contrast matrix 
  mm_EEG_task_RT =  model.matrix( ~ Cong, EEG_task_RT_lmm) 

# Attach to dataframe
  EEG_task_RT_lmm[,(ncol(EEG_task_RT_lmm)+1):(ncol(EEG_task_RT_lmm)+2)] = mm_EEG_task_RT
  names(EEG_task_RT_lmm)[(ncol(EEG_task_RT_lmm)-1):ncol(EEG_task_RT_lmm)] = c("Grand Mean", "Nov_Rep")            

# Build full model with new names                
  mod_RT_EEG.lmer1 = lmer(log(RTs) ~ Nov_Rep + scale(Age) + scale(WM) + 
                            (1 + Nov_Rep ||ID) + 
                            (1 + Nov_Rep ||Stim_Type),                   
                          data = EEG_task_RT_lmm,control=lmerControl(calc.derivs = FALSE), REML = FALSE)

## PCA to check random effect structure (Cut-off: 0.005 - 0.001)

# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_RT_EEG.lmer1))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_RT_EEG.lmer1),comp = "Variance")

# 3rd: remove all terms with zero variance --> comprises final model 
  mod_RT_EEG.lmer2 = lmer(log(RTs) ~ Nov_Rep  + scale(Age) + scale(WM) + 
                          (1 + Nov_Rep||ID) + 
                          (1 |Stim_Type),                   
                        data = EEG_task_RT_lmm,control=lmerControl(calc.derivs = FALSE), REML = FALSE)

# 4th: re-check the model PCA / variance of random factors
  summary(rePCA(mod_RT_EEG.lmer2))
  print(VarCorr(mod_RT_EEG.lmer2),comp = "Variance")

# 5th: Do Likelihood Ratio Test (LRT) - to check whether all random slopes improve the model

# LRT without random slope Nov_Rep for ID
  mod_RT_EEG.lmer3 = lmer(log(RTs) ~ Nov_Rep  + scale(Age) + scale(WM) + 
                          (1 |ID) + 
                          (1 |Stim_Type),                   
                        data = EEG_task_RT_lmm,control=lmerControl(calc.derivs = FALSE), REML = FALSE)

# Calculate ANOVA
  anova(mod_RT_EEG.lmer2,mod_RT_EEG.lmer3)

# LRT without random slope Nov_Rep for Stim_Type
  mod_RT_EEG.lmer4 = lmer(log(RTs) ~ Nov_Rep  + scale(Age) + scale(WM) + 
                            (1 + Nov_Rep||ID) + 
                            (1 |Stim_Type),                   
                          data = EEG_task_RT_lmm,control=lmerControl(calc.derivs = FALSE), REML = FALSE)
  
# Calculate ANOVA
  anova(mod_RT_EEG.lmer2,mod_RT_EEG.lmer4)


# 6th: remove random slopes which did not improve the model 
  mod_RT_EEG.lmer5 = lmer(log(RTs) ~ Nov_Rep  + scale(Age) + scale(WM) + 
                            (1 + Nov_Rep||ID) + 
                            (1 |Stim_Type),                   
                          data = EEG_task_RT_lmm,control=lmerControl(calc.derivs = FALSE), REML = FALSE)

# 7th: re-check the model PCA / variance of random factors
  summary(rePCA(mod_RT_EEG.lmer5))
  print(VarCorr(mod_RT_EEG.lmer5),comp = "Variance")

```

We applied a scaled sum contrast to compare reaction times for novel vs repeated facial expressions. The final model was built as: 

  ``r format(formula(mod_RT_EEG.lmer5))``

##### LMM1: Normality of residuals 

RTs were log-transformed (determined using the Box-Cox procedure) to meet the assumption of normally distributed residuals.

```{r EEG_RT_LMM1_normres, fig.width = 6, fig.asp = .62}

## Check properties of DV / residuals 

# Visualize normality assumption of residuals (without log transform)
  mod_RT_lmm_no_log = lm(RTs ~ Cong, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_no_log = residuals(mod_RT_lmm_no_log)

  par(mfrow=c(1,2))
  qqpl_RT_lmm_no_log = qqPlot(res.mod_RT_lmm_no_log, main="QQplot before transformation")    
  norm_RT_lmm_no_log = plot(density(res.mod_RT_lmm_no_log), main="Density plot before transformation")  
  par(mfrow=c(1,1))

# Check which transformation of DV is suitable

# Calculate box-cox plot
  mod_RT_targ = lm(RTs ~ Cong, data=EEG_task_RT_lmm)
  boxcox(mod_RT_targ)   

# Visualize normality assumption of residuals (with log transform)
  mod_RT_lmm_log = lm(log(RTs) ~ Cong, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_log = residuals(mod_RT_lmm_log)
  
  par(mfrow=c(1,2))
  qqpl_RT_lmm_log = qqPlot(res.mod_RT_lmm_log, main="QQplot after transformation")    
  norm_RT_lmm_log = plot(density(res.mod_RT_lmm_log), main="Density plot after transformation")  
  par(mfrow=c(1,1))
          
```

---

##### LMM1: Homoscedasticity 

Based on the figure, we assume homoscedasticity. 

```{r EEG_RT_LMM1_homosk, fig.width = 5, fig.asp = .62}

                  
# Check homoscedasticity
  plot(fitted(mod_RT_EEG.lmer5), residuals(mod_RT_EEG.lmer5))
  abline(0, 0) 
```    

---

##### LMM2: Random effect structure

```{r EEG_RT_LMM2_build_res}

# Choose outlier-free data and correct answers          
  EEG_task_RT_targ_lmm = subset(EEG_task_data, Response == 1)
  EEG_task_RT_targ_lmm = subset(EEG_task_RT_targ_lmm,Exclude_smaller_250ms == FALSE & Exclude_larger_7s == FALSE & Exclude_MAD == FALSE & EEG_trial_loss == 1)  

# Rename variables 
  EEG_task_RT_targ_lmm$Target[EEG_task_RT_targ_lmm$Target==4] = "hap"
  EEG_task_RT_targ_lmm$Target[EEG_task_RT_targ_lmm$Target==5] = "neu"
  EEG_task_RT_targ_lmm$Target[EEG_task_RT_targ_lmm$Target==6] = "ang"
  EEG_task_RT_targ_lmm$Target[EEG_task_RT_targ_lmm$Target==7] = "hap"
  EEG_task_RT_targ_lmm$Target[EEG_task_RT_targ_lmm$Target==8] = "neu"
  EEG_task_RT_targ_lmm$Target[EEG_task_RT_targ_lmm$Target==9] = "ang"

# Create factors, define neutral as baseline
  EEG_task_RT_targ_lmm$Target = factor(EEG_task_RT_targ_lmm$Target, levels=c("neu","hap","ang"))
  EEG_task_RT_targ_lmm$ID = as.factor(EEG_task_RT_targ_lmm$ID)
  EEG_task_RT_targ_lmm$Stim_Type = as.factor(EEG_task_RT_targ_lmm$Stim_Type)

# Create contrast for emotion
  contrasts(EEG_task_RT_targ_lmm$Target) = contr.treatment(3, base = 1)

# Add contrast columns
  mm_EEG_task_RT_targ =  model.matrix( ~ Target, EEG_task_RT_targ_lmm) 

# Attach to dataframe
  EEG_task_RT_targ_lmm[,(ncol(EEG_task_RT_targ_lmm)+1):(ncol(EEG_task_RT_targ_lmm)+3)] = mm_EEG_task_RT_targ
  names(EEG_task_RT_targ_lmm)[(ncol(EEG_task_RT_targ_lmm)-2):ncol(EEG_task_RT_targ_lmm)] = c("Mean","Hap_Neu", "Ang_Neu")    

## Define model 
  mod_RT_targ.lmer1 = lmer(log(RTs) ~ 
                             Hap_Neu + Ang_Neu + scale(Age) + scale(WM) + 
                             (1 + Hap_Neu + Ang_Neu||ID) +
                             (1 + Hap_Neu + Ang_Neu||Stim_Type),
                           data = EEG_task_RT_targ_lmm,
                           control=lmerControl(calc.derivs = FALSE), REML = FALSE)

# 1st: check how many zero variance terms you got in random effects
  summary(rePCA(mod_RT_targ.lmer1))

# 2nd: check which random terms explain the least variance
  print(VarCorr(mod_RT_targ.lmer1),comp = "Variance")

# 3rd: remove all terms with zero variance --> comprises final model
  mod_RT_targ.lmer2 = lmer(log(RTs) ~ 
                           Hap_Neu + Ang_Neu + scale(Age) + scale(WM) + 
                           (1 |ID) +
                           (0 + Hap_Neu + Ang_Neu||Stim_Type),
                         data = EEG_task_RT_targ_lmm,
                         control=lmerControl(calc.derivs = FALSE), REML = FALSE)

# 4th: re-check the model PCA / variance of random factors
  summary(rePCA(mod_RT_targ.lmer2))
  print(VarCorr(mod_RT_targ.lmer2),comp = "Variance")

# 5th: Likelihood-ratio-testing
# Stim Type
  mod_RT_targ.lmer3 = lmer(log(RTs) ~ 
                           Hap_Neu + Ang_Neu + scale(Age) + scale(WM) + 
                           (1 |ID) +
                           (1 |Stim_Type),
                         data = EEG_task_RT_targ_lmm,
                         control=lmerControl(calc.derivs = FALSE), REML = FALSE)

# Calculate ANOVA  
  anova(mod_RT_targ.lmer2,mod_RT_targ.lmer3)


# Re-check the model PCA / variance of random factors
  summary(rePCA(mod_RT_targ.lmer3))
  print(VarCorr(mod_RT_targ.lmer3),comp = "Variance")
 
```

According to our hypothesis, the main fixed effects of interest was emotion of Face 2. we applied a treatment contrast comparing neutral vs happy and neutral vs angry emotional facial expressions (` Neutral vs Happy`, `Neutral vs Angry`). The final model was comprised of: 

  ``r format(formula(mod_RT_targ.lmer3))``

---


##### LMM2: Normality of residuals 

RTs were log-transformed (determined using the Box-Cox procedure) to meet the assumption of normally distributed residuals.

```{r EEG_RT_LMM2_normres, fig.width = 6, fig.asp = .62}      

## Check properties of DV / residuals 

# Visualize normality assumption of residuals (without log transform)
  mod_RT_lmm_no_log = lm(RTs ~ Target, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_no_log = residuals(mod_RT_lmm_no_log)
  
  par(mfrow=c(1,2))
  qqpl_RT_lmm_no_log = qqPlot(res.mod_RT_lmm_no_log, main="QQplot before transformation")    
  norm_RT_lmm_no_log = plot(density(res.mod_RT_lmm_no_log), main="Density plot before transformation")  
  par(mfrow=c(1,1))

# Check which transformation of DV is suitable 

# Calculate box-cox plot
  mod_resp = lm(RTs ~ Target, data=EEG_task_RT_targ_lmm)
  boxcox(mod_resp)   

# Visualize normality assumption of residuals (with log transform)
  mod_RT_lmm_log = lm(log(RTs) ~ Target, data=EEG_task_RT_targ_lmm)
  res.mod_RT_lmm_log = residuals(mod_RT_lmm_log)
  
  par(mfrow=c(1,2))
  qqpl_RT_lmm_log = qqPlot(res.mod_RT_lmm_log,main="QQplot after transformation")    
  norm_RT_lmm_log = plot(density(res.mod_RT_lmm_log), main="Density plot after transformation")
  par(mfrow=c(1,1))
    
```

---

##### LMM2: Homoscedasticity

Based on the figure, we assume homoscedasticity. 

```{r EEG_RT_LMM2_homosk, fig.width = 5, fig.asp = .62}
# Check homoscedasticity
  plot(fitted(mod_RT_targ.lmer2), residuals(mod_RT_targ.lmer3))
  abline(0, 0)    
```

---

#### **Results**

<!-- Print LMM results -->

Contrary to our hypothesis, we did not find a significant main effect of novelty. Children seemed to be equally fast in detecting novel and repeated facial expression. Trials in which the emotion happy was presented as Face 2 were detected significantly faster compared to neutral faces. No difference between angry and neutral as Face 2 could be found. 

<div align="center">

```{r EEG_RT_LMM_results, results = TRUE}

# Create table
  tab_model(mod_RT_EEG.lmer5, mod_RT_targ.lmer3,
          show.intercept = FALSE,
          pred.labels=labels,
          string.est = "b",
          show.se=TRUE, string.se = "SE",
          show.stat=TRUE, string.stat = "t",
          show.ci = FALSE, 
          show.re.var = TRUE, show.obs = FALSE,
          emph.p = TRUE, dv.labels=c("Face 2 Novelty","Face 2 Emotion") , show.icc = TRUE)
```

</div>

<br>

*Note:* p-values for the fixed effects calculated using Wald-statistics approximation, uncorrected. *b*: unstandardized coefficient; *SE*: standard error; *t*: test statistic coefficient; *p*: p-value; *σ2*: within-group variance; *τ00*: between-group variance; *ICC*: interclass correlation (ratio of between-cluster variance to total variance); *N*: number of random effects. 

```{r save_models, include = FALSE, eval = FALSE}

# Save data set in RData format
  save(mod_Acc_EEG.glmm4, file = "./data/mod_Acc_EEG.glmm4.RData")
  save(mod_Acc_targ.glmm5, file = "./data/mod_Acc_targ.glmm5.RData")
  save(mod_RT_EEG.lmer5, file = "./data/mod_RT_EEG.lmer5.RData")
  save(mod_RT_targ.lmer3, file = "./data/mod_RT_targ.lmer3.RData")
    
```


# Session info

<!-- Provide session info  -->

```{r session_info, results = TRUE}

# Get session info 
  sessionInfo()

```



