---
title: "Delayed match-to-sample task"
output: 
  rmdformats::material:
    highlight: kate
    css: web_style.css
    thumbnails: false
    lightbox: true
    gallery: true
    cards: true
    self_contained: no
    number_sections: no
    code_folding: hide
    fig_caption: yes
---

<!-- Set up workspace -->

```{r setup, include = FALSE, message = FALSE, warning = FALSE}

# Set general settings for Markdown file 
  options(max.print="75")

  knitr::opts_chunk$set(echo=TRUE,
  	             #cache=TRUE,
                 prompt=FALSE,
                 tidy=TRUE,
                 comment=NA,
                 message=FALSE,
                 warning=FALSE,
                 results = FALSE,
  	             fig.align="center",
  	             fig.width=6, fig.height=4)
  knitr::opts_knit$set(width=75)
  
# Swipe environment
  rm(list=ls())
  
# Set libraries
  library(cowplot)
  library(dplyr)
  library(EnvStats)
  library(ez)
  library(ggplot2)
  library(ggstatsplot)
  library(Hmisc)
  library(kableExtra)
  library(lme4)
  library(lmerTest)
  library(MASS)
  library(miceadds)
  library(multcomp)
  library(psych)
  library(reshape2)
  library(Rmisc)
  library(sjPlot)
  library(sjmisc)
  library(sjlabelled)
  library(tidyverse)

# Load overdispersion function
  overdisp_fun = function(model) {
    rdf = df.residual(model)
    rp = residuals(model,type="pearson")
    Pearson.chisq = sum(rp^2)
    prat = Pearson.chisq/rdf
    pval = pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
    c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
  }
  
# Raincloud plot function   
  source("./functions/geom_flat_violin.R")
  
# Round to 2 digits   
  options(digits=3)
  
# Disable scientific notation in R
  options(scipen = 999)
  
# Set figure theme  
  theme_SN = theme(axis.title.y = element_text(size = 13, margin = margin(t = 0, r = 20, b = 0, l = 0)),
          panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank(),
          panel.grid.major.y = element_line(colour = "black", linetype = "dotted", size=0.6),
          panel.grid.minor.y = element_blank(),
          panel.background = element_rect(colour = "black", size = 0.5),
          text=element_text(size = 12),
          legend.position = "none")
  
# Set figure color palettes
  emotion_col = c("#99bada","#3375b5","#003162")
  nov_col = c("#2FA9F5","#134462")
  
# Round p-values   
  reportP = function(pValue){
    if (pValue < 0.001){
      result = "*p* < 0.001"
    } else {
      result = sprintf("*p* = %.2f", pValue) # inserts a float into a string and simultaneously do rounding
    }
    return(result)
  }  
  
# Beta values
  reportbe = function(pValue){
    if (0 <= pValue & pValue <= 0.01 ){
      result = "< 0.01"
    } 
    else if (pValue < 0){
      result = sprintf("= %.2f", pValue)
    }
    else {
      result = sprintf("= %.2f", pValue) # inserts a float into a string and simultaneously do rounding
    }
    return(result)
  }  
  
# CI values
  reportci = function(pValue){
    if (0 <= pValue & pValue <= 0.01 ){
      result = "< 0.01"
    } 
    else if (pValue < 0){
      result = sprintf("%.2f", pValue)
    }
    else {
      result = sprintf("%.2f", pValue) # inserts a float into a string and simultaneously do rounding
    }
    return(result)
  }    
  
```

<!-- Load data set-->

```{r load_data, include = FALSE}

# Load EEG task data
  load.Rdata(filename="./data/EEG_task_data.Rdata", "EEG_task_data")

# Scale WM
  EEG_task_data$WM_scal = scale(EEG_task_data$WM)
  
```

# Task description

Our EEG paradigm was a delayed match-to-sample task in which children had do indicate whether Face 1 and Face 2 showed the same (`repeated`) or a different emotional facial expression (`novel`). Besides their EEG, we measured participants' accuracy rates and reaction times. 

We excluded reaction times < 250 ms and incorrect trials. Subsequently, we calculated general linear mixed models (GLMM) for accuracy rates and linear mixed models (LMM) for reaction times. Fixed effects are defined for each model individually.  As fixed factors, all models included treatment contrasts for *facial expressions* (`emotional [average of happy/angry] vs. neutral faces (Emo_Neu)`, `happy vs. angry faces (Hap_Ang)`), *repetition* (`novel vs. repeated emotion trials (Rep_Nov)`) as well as their interaction (`Emo_NeuxRep_Nov, Hap_AngxRep_Nov`). Due to the high cognitive task demands, working memory  (`WM_scal`) was entered as scaled covariate in all (general) linear mixed model analyses. The random effects structure included random intercepts for participants `(1|ID)` and stimulus `(1|Stim_Type)`. Assumptions for multiple regression were checked for all models (normality of the residuals, linearity, multicollinearity, homoscedasticity). 

We expected children to be faster and more accurate when Face 1 and Face 2 showed different emotions. Additionally, we expected the highest accuracy rates and fastest reaction times for pairings with happy facial expressions.

# Accuracy & Reaction times

## **Descriptive statistics** 

Accuracy rates (left side) and reaction times (right side) of the delayed match-to-sample task. Error bars indicate standard errors (SE).

```{r EEG_Acc_RT_plots, results = TRUE, fig.width = 8, fig.height = 4}

## Plot accuracy rates 
  EEG_task_Acc_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE & Response == 1)

# Rename variables
  EEG_task_Acc_plot$Cong[EEG_task_Acc_plot$Cong == 1] = "repeated"
  EEG_task_Acc_plot$Cong[EEG_task_Acc_plot$Cong == 2] = "novel"

  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==4] = "happy"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==5] = "neutral"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==6] = "angry"
  
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==7] = "happy"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==8] = "neutral"
  EEG_task_Acc_plot$Target[EEG_task_Acc_plot$Target==9] = "angry"

# Get accuracy for novel and repeated Target
  acc_all = data.frame(xtabs(~ID+Cong+Target, EEG_task_Acc_plot))

# Recode to accuracy in percent (72 novel trials, 72 repeated trials, divided by three for three emotion conditions)
  acc_all$Freq = (acc_all$Freq/24)*100

# Factor Target
  acc_all$Cong = as.factor(acc_all$Cong)
  acc_all$Target = as.factor(acc_all$Target)

# Calculate descriptives on accuracy
  stats_acc_all = summarySEwithin(acc_all, measurevar ="Freq", withinvars=c("Cong","Target"), idvar = "ID")

# Plot accuracy
  EEG_acc_plot = ggplot(stats_acc_all, aes(x=Target, y=Freq, fill = Cong)) +
    geom_bar(position=position_dodge(), stat="identity",colour="black", size=0.4,width=0.9) +
    geom_errorbar(aes(ymin=Freq-se, ymax=Freq+se), size=0.4, width=0.2, position=position_dodge(.9)) +
    labs (x= "", y = "Accuracy [%]") +
    scale_fill_manual(name = "Repetition", values=nov_col)+
    coord_cartesian(ylim = c(0, 80)) +
    scale_y_continuous(breaks=seq(0,100,20))+
    theme_bw()+
    theme_SN +
    theme(legend.position = "top", legend.direction = "vertical",
           legend.key.size = unit(1, "cm"),
           legend.key.width = unit(0.5,"cm"))
   
## RT plot

# Choose outlier-free and correct trial data
  EEG_task_RT_plot = subset(EEG_task_data, Exclude_smaller_250ms == FALSE & Response == 1)

# Rename variables
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==1] = "repeated"
  EEG_task_RT_plot$Cong[EEG_task_RT_plot$Cong==2] = "novel"

  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==4] = "happy"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==5] = "neutral"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==6] = "angry"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==7] = "happy"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==8] = "neutral"
  EEG_task_RT_plot$Target[EEG_task_RT_plot$Target==9] = "angry"
  
  stats_RT_all = summarySEwithin(EEG_task_RT_plot, measurevar="RTs", withinvars=c("Cong","Target"), idvar = "ID")
  
# Plot RTs
  EEG_RT_plot =
    ggplot(stats_RT_all, aes(x = Target, y = RTs, fill = Cong)) +
    geom_bar(position=position_dodge(), stat="identity", colour="black", size=0.4, width=0.9) +
    geom_errorbar(aes(ymin=RTs-se, ymax=RTs+se), size=0.4, width=0.2, position=position_dodge(.9)) +
    labs (x= "", y = "RT [ms]") +
    coord_cartesian(ylim = c(0, 3000)) +
    scale_y_continuous(breaks=seq(0,3000,500))+
    scale_fill_manual(values=nov_col)+
    theme_bw()+
    theme_SN+
    theme(legend.position = "none", legend.title=element_blank())

# Put plots together
  plots_Acc_RT = cowplot::plot_grid(
    EEG_acc_plot + theme(legend.position="none"),
    EEG_RT_plot + theme(legend.position="none"),
    align = 'vh',
    hjust = -1,
    nrow = 1)

# Get legend
  legend_Acc_RT = get_legend(EEG_acc_plot  +
    theme(legend.box.margin = margin(0, 0, 0, 2)))

# Display plot: https://wilkelab.org/cowplot/articles/shared_legends.html
  fig_EEG_Acc_RT = cowplot::plot_grid(plots_Acc_RT, legend_Acc_RT, rel_widths = c(1, .2))
  fig_EEG_Acc_RT
  
  
# Save figure for publication   
  #ggsave("Figure_X_DMTST_perf.tiff", plot = last_plot(), dpi = 300)

```

```{r EEG_trial_loss, eval = FALSE, include = FALSE}

## Get differences between trials
  trial_stats = acc_all

  library(data.table)

 # rep_trials = as.data.table(trial_stats)[, sum(Freq), by = .(ID, Cong)]
  emo_trials = as.data.table(trial_stats)[, sum(Freq), by = .(ID, Target)]
  
#   rep_trials = as.data.table(trial_stats)[, sum(Freq), by = .(ID, Cong, Target)]
#   
#     
# # Calculate condtional mean 
#   rep_trials_2 =  aggregate(rep_trials$V1, FUN=sd, 
#           by=list(emotion=rep_trials$Target, repetition=rep_trials$Cong))  
#   
#   
#   rep_trials_2
# 
#   # Calculate mean and SD   
#   tr_mean_rep = tapply(rep_trials$V1,rep_trials$Cong,mean)
#   tr_sd_rep = tapply(rep_trials$V1,rep_trials$Cong,sd)
#   
#   tr_mean_rep
#   tr_sd_rep 
#   
# # Paired-samples t-test
#   t_test_res = t.test(rep_trials$V1[rep_trials$Cong=="repeated"],
#                       rep_trials$V1[rep_trials$Cong=="novel"],
#                       paired = TRUE, alternative = "two.sided")
#   
#   t_test_res
  
  
# REPORTING IN PAPER EMOTION EFFECTS (for repetition effects see Script 2)
  tr_mean_emo = tapply(emo_trials$V1,emo_trials$Target,mean)
  tr_sd_emo = tapply(emo_trials$V1,emo_trials$Target,sd)
  
  tr_mean_emo
  tr_sd_emo

# Calculate one-way ANOVA to test equality of trial numbers
  emo.aov = aov(V1 ~ Target, data = emo_trials)

# Extract values to present 
  emo.aov.sum = summary(emo.aov)
  emo.aov.sum = data.frame(emo.aov.sum[[1]])
  
  emo.aov.sum

```

## **Model specifications** 

### Accuray rate GLMM: {.tabset .tabset-pills}

<!-- GLMM model specifications -->

#### Random effect structure 

We fitted single-trial data to the following model:

```{r EEG_Acc_GLMM_res}

# Select outlier-free data
  EEG_task_Acc_glmm = subset(EEG_task_data, Exclude_smaller_250ms == FALSE)

# Scale working memory
  EEG_task_data$WM_scal = scale(EEG_task_data$WM)

# Factor random effects
  EEG_task_Acc_glmm$ID = as.factor(EEG_task_Acc_glmm$ID)
  EEG_task_Acc_glmm$Stim_Type = as.factor(EEG_task_Acc_glmm$Stim_Type)

# Define novel vs repeated trials
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 4]='c_happy';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 5]='c_neutral';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 6]='c_angry';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 7]='ic_happy';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 8]='ic_neutral';
  EEG_task_Acc_glmm$Target[EEG_task_Acc_glmm$Target == 9]='ic_angry';

# Create one variable for emotion and one for repetition 
  EEG_task_Acc_glmm$emot[(EEG_task_Acc_glmm$Target == 'c_happy')  | (EEG_task_Acc_glmm$Target == 'ic_happy')] = 1
  EEG_task_Acc_glmm$emot[(EEG_task_Acc_glmm$Target == 'c_angry')  | (EEG_task_Acc_glmm$Target == 'ic_angry')] = 2
  EEG_task_Acc_glmm$emot[(EEG_task_Acc_glmm$Target == 'c_neutral')  | (EEG_task_Acc_glmm$Target == 'ic_neutral')] = 3
  
  EEG_task_Acc_glmm$rep[(EEG_task_Acc_glmm$Target == 'c_happy')  
                        | (EEG_task_Acc_glmm$Target == 'c_angry') 
                        | (EEG_task_Acc_glmm$Target == 'c_neutral')] = 1
  EEG_task_Acc_glmm$rep[(EEG_task_Acc_glmm$Target == 'ic_happy')  
                        | (EEG_task_Acc_glmm$Target == 'ic_angry') 
                        | (EEG_task_Acc_glmm$Target == 'ic_neutral')] = 2

# Rename variables   
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 1]='happy';
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 2]='angry';
  EEG_task_Acc_glmm$emot[EEG_task_Acc_glmm$emot == 3]='neutral';
  EEG_task_Acc_glmm$rep[EEG_task_Acc_glmm$rep == 1]='repeated';
  EEG_task_Acc_glmm$rep[EEG_task_Acc_glmm$rep == 2]='novel';

# Factor emotion and repetition variable
  EEG_task_Acc_glmm$rep = factor(EEG_task_Acc_glmm$rep)
  EEG_task_Acc_glmm$emot = factor(EEG_task_Acc_glmm$emot) 

# Create contrasts 
  contrasts(EEG_task_Acc_glmm$rep) = c(-0.5,0.5) # intercept is the mean of happy and angry
  contrasts(EEG_task_Acc_glmm$emot) = contr.treatment(3,  base = 3)

# A = angry, N = neutral, H = happy
  HvsA = c(0.5,-0.5,0) # compare: happy vs. angry
  EvsN = c(-0.25,-0.25,0.5) # compare happy/angry to neutral 
  
  contrasts(EEG_task_Acc_glmm$emot) = cbind(EvsN,HvsA)
  
# Final model
  mod_Acc_EEG.glmm = glmer(Response ~ emot*rep + WM_scal +  
                            (1 |ID) + 
                            (1|Stim_Type), 
                            data = EEG_task_Acc_glmm,control=glmerControl(calc.derivs = FALSE),
                            family = binomial)
          
```

 ``r format(formula(mod_Acc_EEG.glmm))``
 
---

#### Overdispersion

If the p-value is < 0.05, data would be overdispersed. Here p > 0.05. Hence, overdispersion is not a problem.

```{r EEG_Acc_GLMM_overd_1, results = TRUE}

# Assumption check: Appropriate estimation of variance - check for overdispersion
  overdisp_fun(mod_Acc_EEG.glmm)

```

---


### Reaction time LMM: {.tabset .tabset-pills}

#### Random effect structure

<!-- LMM model specifications -->

The final model was: 

```{r EEG_RT_LMM_build_res}

# Choose outlier-free data and correct answers    
  EEG_task_RT_lmm = subset(EEG_task_data,  Response == 1 & Exclude_smaller_250ms == FALSE)

# Define novel vs repeated trials
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 4]='c_happy';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 5]='c_neutral';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 6]='c_angry';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 7]='ic_happy';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 8]='ic_neutral';
  EEG_task_RT_lmm$Target[EEG_task_RT_lmm$Target == 9]='ic_angry';

# Create one variable for emotion and one for repetition 
  EEG_task_RT_lmm$emot[(EEG_task_RT_lmm$Target == 'c_happy')  | (EEG_task_RT_lmm$Target == 'ic_happy')] = 1
  EEG_task_RT_lmm$emot[(EEG_task_RT_lmm$Target == 'c_angry')  | (EEG_task_RT_lmm$Target == 'ic_angry')] = 2
  EEG_task_RT_lmm$emot[(EEG_task_RT_lmm$Target == 'c_neutral')  | (EEG_task_RT_lmm$Target == 'ic_neutral')] = 3
  
  EEG_task_RT_lmm$rep[(EEG_task_RT_lmm$Target == 'c_happy')  | (EEG_task_RT_lmm$Target == 'c_angry') | (EEG_task_RT_lmm$Target == 'c_neutral')] = 1
  EEG_task_RT_lmm$rep[(EEG_task_RT_lmm$Target == 'ic_happy')  | (EEG_task_RT_lmm$Target == 'ic_angry') | (EEG_task_RT_lmm$Target == 'ic_neutral')] = 2

# Rename variables   
  EEG_task_RT_lmm$emot[EEG_task_RT_lmm$emot == 1]='happy';
  EEG_task_RT_lmm$emot[EEG_task_RT_lmm$emot == 2]='angry';
  EEG_task_RT_lmm$emot[EEG_task_RT_lmm$emot == 3]='neutral';
  EEG_task_RT_lmm$rep[EEG_task_RT_lmm$rep == 1]='repeated';
  EEG_task_RT_lmm$rep[EEG_task_RT_lmm$rep == 2]='novel';

# Factor variables
  EEG_task_RT_lmm$rep = factor(EEG_task_RT_lmm$rep)
  EEG_task_RT_lmm$emot = factor(EEG_task_RT_lmm$emot) 

# Create contrasts 
  contrasts(EEG_task_RT_lmm$emot) = contr.treatment(3,  base = 3)
  contrasts(EEG_task_RT_lmm$rep) = c(-0.5,0.5)

# A = angry, N = neutral, H = happy
  HvsA = c(0.5,-0.5,0) # compare: happy vs. angry
  EvsN = c(-0.25,-0.25,0.5) # compare happy/angry to neutral 
  contrasts(EEG_task_RT_lmm$emot) = cbind(EvsN,HvsA)
  
  mod_RT_EEG.lmer = lmer(log(RTs) ~ emot*rep + WM_scal +
                                   (1 |ID) +
                                   (1 |Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))
  
```

  ``r format(formula(mod_RT_EEG.lmer))``

#### Normality of residuals 

RTs were log-transformed (determined using the Box-Cox procedure) to meet the assumption of normally distributed residuals.

```{r EEG_RT_LMM1_normres, fig.width = 6, fig.asp = .62}

# Visualize normality assumption of residuals (without log transform)
  mod_RT_lmm_no_log = lm(RTs ~ Cong, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_no_log = residuals(mod_RT_lmm_no_log)

  par(mfrow=c(1,2))
  qqpl_RT_lmm_no_log = qqPlot(res.mod_RT_lmm_no_log, main="QQplot before transformation")    
  norm_RT_lmm_no_log = plot(density(res.mod_RT_lmm_no_log), main="Density plot before transformation")  
  par(mfrow=c(1,1))

# Check which transformation of DV is suitable

# Calculate box-cox plot
  mod_RT_targ = lm(RTs ~ Cong, data=EEG_task_RT_lmm)
  boxcox(mod_RT_targ)   

# Visualize normality assumption of residuals (with log transform)
  mod_RT_lmm_log = lm(log(RTs) ~ Cong, data=EEG_task_RT_lmm)
  res.mod_RT_lmm_log = residuals(mod_RT_lmm_log)
  
  par(mfrow=c(1,2))
  qqpl_RT_lmm_log = qqPlot(res.mod_RT_lmm_log, main="QQplot after transformation")    
  norm_RT_lmm_log = plot(density(res.mod_RT_lmm_log), main="Density plot after transformation")  
  par(mfrow=c(1,1))
          
```

---

#### Homoscedasticity 

We assume homoscedasticity based on visual inspection. 

```{r EEG_RT_LMM1_homosk, fig.width = 5, fig.asp = .62}

# Check homoscedasticity
  plot(fitted(mod_RT_EEG.lmer), residuals(mod_RT_EEG.lmer))
  abline(0, 0) 
```    

---

## **Results**

```{r EEG_task_post_hoc_calc, results = "asis"}

# Calculate post-hoc tests
  EEG_task_RT_lmm$interaction = interaction(EEG_task_RT_lmm$rep, EEG_task_RT_lmm$emot)

  mod_RT_EEG.lmer_model =   lmer(log(RTs) ~ interaction + WM_scal +
                                   (1 |ID) +
                                   (1 |Stim_Type),
                                   data = EEG_task_RT_lmm,
                                   control=lmerControl(calc.derivs = FALSE))
  
# Choose contrasts of interest / add fdr-correction
  
  
# Choose contrasts of interest / add fdr-correction
  mod_RT_EEG.lmer_model_posthoc =  summary(glht(mod_RT_EEG.lmer_model, linfct=mcp(interaction = c(
                                                        "repeated.neutral - repeated.angry = 0",
                                                        "novel.neutral - novel.angry = 0",
                                                        "novel.neutral - novel.happy = 0",
                                                        "repeated.neutral - repeated.happy = 0")), test = adjusted(type = "fdr")))
  
# Get ready for presentation in RMarkdown
  tab1 = merge(as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$coefficients),as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$sigma),by=0)
  tab2 = as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$pvalues)
  rownames(tab2) = rownames(as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$tstat))
  tab2 = merge(as.data.frame(mod_RT_EEG.lmer_model_posthoc$test$tstat),tab2,by=0)
  post_hoc_tests_EEG_RT = merge(tab1,tab2,by='Row.names')
  colnames(post_hoc_tests_EEG_RT) = c("Contrast","Est.","Std. Error", "z value", "p value")

  
```

<div align="center">

```{r EEG_Acc_RT_GLMM_results, results = 'asis'}
# Create labels
  labels = c("Emotion vs. Neutral", "Happy vs. Angry", "Repetition", "Working Memory", "E vs. N x Repetition ", "H vs. A x Repetition")

# Create table
  tab_model(mod_Acc_EEG.glmm, mod_RT_EEG.lmer, show.intercept = FALSE,
          pred.labels= labels, show.ci = FALSE,
          show.se = TRUE, string.se = "SE",
          show.stat = TRUE, string.stat = "t",
          show.re.var = TRUE, show.obs = FALSE,
          emph.p = TRUE, dv.labels=c("Accuracy", "Reaction time") , show.icc = TRUE)
  
```

</div>

<br>

*Note:* p-values for the fixed effects calculated using Wald-statistics approximation, uncorrected. *SE*: standard error; *t*: test statistic coefficient; *p*: p-value; *σ2*: within-group variance; *τ00*: between-group variance; *ICC*: interclass correlation (ratio of between-cluster variance to total variance); *N*: number of random effects. 

<br>


**Post-hoc tests for Reaction time: Emotional vs. Neutral faces vs Repetition contrast**

```{r EEG_RT_post_hoc, results = "asis"}

# Create table
  kable(post_hoc_tests_EEG_RT) %>% 
    kable_styling(bootstrap_options = c("hover"), font_size = 14,fixed_thead = T)  

```

```{r save_models, include = FALSE, eval = FALSE}

# Save data set in RData format
  save(mod_Acc_EEG.glmm, file = "./data/mod_Acc_EEG.glmm.RData")
  save(mod_RT_EEG.lmer, file = "./data/mod_RT_EEG.lmer.RData")
  save(post_hoc_tests_EEG_RT, file = "./data/post_hoc_tests_EEG_RT.RData")
    
```

# Session info

<!-- Provide session info  -->

```{r session_info, results = TRUE}

# Get session info 
  sessionInfo()

```
